### 2016-12-11 paper_mnras/paper.tex
adding mnras template and renaming ass template

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
% \documentclass[a4paper,fleqn,usenatbib]{mnras}
\documentclass[fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
% \usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
% macros. please check here before defining something new.
\input{../paper_resources/macros/code}
\input{../paper_resources/macros/derivatives}
\input{../paper_resources/macros/nuclides}
\input{../paper_resources/macros/concepts}
\input{../paper_resources/macros/units}
\input{../paper_resources/macros/vectors}
\input{../paper_resources/macros/formatting}
\input{../paper_resources/macros/symbols}

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%
% misc. abbreviations
\newcommand{\paperone}{Paper~I} % the first paper

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% NuGrid/MESA way
%%
% see https://en.wikibooks.org/wiki/LaTeX/Colors for selection of
% colors, such as Apricot Aquamarine BlueGreen BurntOrange
% CornflowerBlue Emerald Gray Lavender Maroon NavyBlue Orchid Plum Red
% RoyalBlue SeaGreen Tan Violet YellowOrange

% for comments
\newcommand{\shortcomment}[3]{\textcolor{#1}{[#2: #3]}}
% for the Ready-To-Read sign off
\newcommand{\rtr}[1]{\shortcomment{red}{RTR}{#1}}
% for freezing a section
\newcommand{\sectionisfrozen}[1]{\textcolor{BlueViolet}{\textsf{\bfseries[section is frozen: send comments to #1]}}}
\newcommand{\sectionisdone}{\textcolor{Green}{\textsf{\bfseries[section is done]}}}

% if you want to embed comments in the text, clone the following with
% a color and your initials...

% for author's comments; choose your own color and replace 'fh' and
% 'FH' with your name and initials
\newcommand{\fhcom}[1]{\shortcomment{PineGreen}{FH}{#1}}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[K. T. Smith et al.]{
Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
A. N. Other,$^{2,\dagger}$
Third Author$^{2,3}$
and Fourth Author$^{3}$
\\
% List of institutions
$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country\\
$^\dagger$NuGrid collaboration}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

This is a simple template for authors to write new MNRAS papers.
See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
for a full user guide.

All papers should start with an Introduction section, which sets the work
in context, cites relevant earlier studies in the field by \citet{1996ApJ...456..902R},
and describes the problem the authors aim to solve \citep[e.g.][]{cyburt:10}.

\section{Methods, Observations, Simulations etc.}

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

An example figure can be seen in \Fig{mass-N14}.
, and tables as
e.g. \Tab{example_table}.

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \lFig{mass-N14}
\end{figure}

Another results is also good \Fig{mass-O16}.
% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\lTab{example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{figs/figure_template/mass-O16}
    \caption{Another figure.}
    \lFig{mass-O16}
\end{figure}

\section{Conclusions}

The last numbered section should briefly summarise what has been done, and describe
the final conclusions which the authors draw from their work.

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{../paper_resources/bib/nugrid} % if your bibtex file is
                                             % called example.bib

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the
flow of the main paper, it can be placed in an Appendix which appears
after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2018-06-13 paper_mnras/paper.tex
default is to turn newtxtext on
mnras template works on astrohub.uvic.ca
add color to comment

@@
 % out the following line
-% \usepackage{newtxtext,newtxmath}
+%\usepackage{newtxtext,newtxmath}
 % Depending on your LaTeX fonts installation, you might get better results with one of these:
@@
 % 'FH' with your name and initials
-\newcommand{\fhcom}[1]{\shortcomment{PineGreen}{FH}{#1}}
+\usepackage[usenames,dvipsnames]{color}
+\usepackage[]{color}
+\newcommand{\fhcom}[1]{{\color{PineGreen}[\emph{FH: #1}]}}
+\newcommand{\fhtxt}[1]{{\color{PineGreen}[FH: #1]}}
 
@@
   % or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
-    \caption{This is an example figure. Captions appear below each figure.
-	Give enough detail for the reader to understand what they're looking at,
-	but leave detailed discussion to the main body of the text.}
+
+  %\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
+  \caption{This is an example figure. Captions appear below each
+    figure.  Give enough detail for the reader to understand what
+    they're looking at, but leave detailed discussion to the main body
+    of the text.  This particular figure file will appear when you
+    exectute the example notebook in
+    \texttt{figs/figure\_template}. Then uncomment the
+    \texttt{includegraphics} command in the latex source file.} 
     \lFig{mass-N14}

### 2019-09-28 paper_mnras/paper.tex
add sec 2.1

@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+We present a new method to calculate comprehensive nucleosyntheis in 1D based on mixing information extracted from 3d.
+
 \end{abstract}
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+[David]
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{1996ApJ...456..902R},
-and describes the problem the authors aim to solve \citep[e.g.][]{cyburt:10}.
+[1.5 - 2 pages]
 
-\section{Methods, Observations, Simulations etc.}
+[2 days][2: Sep 4]
 
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+Purpose of introduction is:
+\begin{itemize}
+\item why is the topic important, why should you - the reader - care: absence of any detailed nucleosythesis from recently presented sims from other groups.
+\item why is your contribution (as presented in this paper) needed; you show that by summarizing the state of the art and pointing out why that is insufficient
+\item in Ritter+ and Denissenkov+ a diffusion approach was used, in the Ritter case we only used "typical" diffusion coeffiencts and in Pavel's paper we post-processed the MLT stellar evolution, so here we explore diffusion and advection post-processing;
+\item the approach is based on .... include brief summary of conveyer belt method as published in recent Monash paper
+\item Define the scope of the paper: This paper will go a first toward addressing these issues.
+It will present and compare two ways to perform 1D burn+mix  post-processing of 3D hydro.
+The first adopts the diffusion coefficient method, and the second the conveyor-belt advection method.
+Both methods will be applied to 3D hydrodynamic simulations of RAWDs and the goal is to reproduce the spherically averaged radial profile evolution of the ingested H.
+In the future this method can then be applied to comprehensive post-processing using large networks.
+\end{itemize}
 
-\subsection{Maths}
-\label{sec:maths} % used for referring to this section from elsewhere
+\section{Methods}
+\label{sec:allmethods}
 
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
+\subsection{PPMstar simulations}
+The advective post-processing method introduced here is applied to 3D hdyrodynamic simulations of He-shell flash convection in a rapidly accreting white dwarf \citep{Denissenkov:2017ba}.
+The initial stratification has been taken from stellar evolution model G with metallicity $\mathrm{[Fe/H]} = -2.6$ from \cite{2019MNRAS.488.4258D}.
 
-\begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
-\end{equation}
+As in previous work \citep{Herwig:2014cx,Jones:2017kc} we use the \ppmstar{} code of \citet{woodward15} with additional details provided by \citet{Andrassy:2018wy}. The explicit
+Cartesian-grid-based code is based on the
+Piecewise-Parabolic Method \citep[PPM;][]{woodward_colella81,
+woodward_colella84, colella_woodward84, woodward86, woodward07}, and  tracks the advection of concentrations in a two-fluid scheme using the Piecewise-Parabolic Boltzmann method \citep[PPB;][]{woodward86,woodward15}.
 
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
+\subsection{Diffusion post-processing}
+Robert, Pavel, Falk
 
-\subsection{Figures and tables}
+\begin{itemize}
+\item briefly describe work flow, based on D determination already dewscribed in Jones+ (maybe with some input on updated from Robert)
+\end{itemize}
 
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
+\subsection{Advection post-processing}
 
-An example figure can be seen in \Fig{mass-N14}.
-, and tables as
-e.g. \Tab{example_table}.
+[David]
 
-% Example figure
-\begin{figure}
-  % To include a figure from a file named example.*
-  % Allowable file formats are eps or ps if compiling using latex
-  % or pdf, png, jpg if compiling using pdflatex
+[2-3 pages]
 
-  %\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
-  \caption{This is an example figure. Captions appear below each
-    figure.  Give enough detail for the reader to understand what
-    they're looking at, but leave detailed discussion to the main body
-    of the text.  This particular figure file will appear when you
-    exectute the example notebook in
-    \texttt{figs/figure\_template}. Then uncomment the
-    \texttt{includegraphics} command in the latex source file.} 
-    \lFig{mass-N14}
-\end{figure}
+[5 days][1: Sep 2]
 
-Another results is also good \Fig{mass-O16}.
-% Example table
-\begin{table}
-	\centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\lTab{example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
+\begin{itemize}
+\item provide a formal description of the method
+\item do not discuss, don't pros and cons
+\item no results yet
+\item do write down all equations and clear definitions of all quantities and concepts
+\end{itemize}
 
-% Example figure
-\begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{figs/figure_template/mass-O16}
-    \caption{Another figure.}
-    \lFig{mass-O16}
-\end{figure}
+\section{Results}
+\subsection{3D hydrodynamic simulations of RAWDs}
 
-\section{Conclusions}
+[David]
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+[2.5 pages]
+
+[3 days][3: Sep 9]
+
+\begin{itemize}
+\item describe the properties of the flow that matters for advection scheme
+\item asymmetry of flow, entrainment rate
+\item transition from convection to stable, 
+\end{itemize}
+
+Figures: (just add the version that you already have)
+\begin{itemize}
+\item mollweide plots of abundance and velocicities
+\item comparison 1536 vs 768
+\end{itemize}
+
+\subsection{Diffusion  post-processing}
+
+[Robert, Pavel, Falk]
+
+[1 pages]
+
+\subsection{Advection post-processing}
+
+[David]
+
+[3-4 pages]
+
+[5 days][4: Sep 13]
+
+\subsubsection{Verification}
+Very brief demonstration of advection with Gaussian. (May in the end have to move to appendix)
+
+\subsubsection{RAWD application}
+Present the application of the conveyer belt method.
+\begin{itemize}
+\item power spectra
+\item time scale plots
+\item stream plots
+\item compare burning rates and locations
+\item steady-state solution
+\end{itemize}
+
+\section{Discussion Conclusions}
+
+[David]
+
+[1-2 pages]
+
+[1 day][5: Sep 16]
+
+\begin{itemize}
+\item short summary of what has been done, highlighting the most important points
+\item self critique, challenges, what remains open and unsolved
+\item limitation: has to be explicit, hint at implications of that finding for application stellar evolution codes
+\item possible future applications beyond rawd
+\end{itemize}
 

### 2021-05-01 paper_mnras/paper.tex
add ulem package
updates
clean template

--- 2018-06-13 paper_mnras/paper.tex
@@
 % Only include extra packages if you really need them. Common packages are:
+\usepackage{rotating}
 \usepackage{graphicx}	% Including figure files
@@
 \usepackage{amssymb}	% Extra maths symbols
+\usepackage{booktabs}
+\usepackage{natbib}
+% \usepackage[dvipsnames]{xcolor}
+\usepackage{textcomp}
+\usepackage{xfrac}
+\usepackage{afterpage}
+\usepackage[normalem]{ulem}
+\usepackage{threeparttable} % modify table
+
 % macros. please check here before defining something new.
@@
 \newcommand{\fhtxt}[1]{{\color{PineGreen}[FH: #1]}}
+\newcommand{\racom}[1]{{\color{Brown}[\emph{RA: #1}]}}
+\newcommand{\ratxt}[1]{{\color{Brown}[RA: #1]}}
+\newcommand{\dscom}[1]{{\color{Red}[\emph{DS: #1}]}}
+\newcommand{\dstxt}[1]{{\color{Red}[DS: #1]}}
+
+% new commands
+\newcommand{\cldfluid}{fluid above the convection zone}
+\newcommand{\airfluid}{convective fluid}
+\newcommand{\ppmstar}{\code{PPMstar}}
 
@@
 % Keep the title short and informative.
-\title[Short title, max. 45 characters]{MNRAS \LaTeXe\ template -- title goes here}
-
+\title[3D1D modeling of the convective-reactive mixing in RAWDs]{3D1D
+  modeling of the convective-reactive mixing in RAWDs} \title[3D1D
+  modeling of the convective-reactive mixing in RAWDs]{3D1D
+  hydro-nucleosynthesis simulations. I. Advective-reactive
+  post-processing method and its application to H ingestion into He-shell
+  flash convection in rapidly accreting white dwarfs}
 % The list of authors, and the short list which is used in the headers.
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[K. T. Smith et al.]{
-Keith T. Smith,$^{1}$\thanks{E-mail: mn@ras.org.uk (KTS)}
-A. N. Other,$^{2,\dagger}$
-Third Author$^{2,3}$
-and Fourth Author$^{3}$
-\\
+\author[D. Stephens et al.]{
+David Stephens,$^{1}$
+Falk Herwig,$^{1,2,\dagger}$\thanks{E-mail: fherwig@uvic.ca}
+Paul Woodward,$^{2,3}$
+Pavel Denissenkov,$^{1,2,\dagger}$
+\newauthor
+ Robert Andrassy$^{4,1}$ 
+and Huaqing Mao$^{3}$\\
 % List of institutions
-$^{1}$Royal Astronomical Society, Burlington House, Piccadilly, London W1J 0BQ, UK\\
-$^{2}$Department, Institution, Street Address, City Postal Code, Country\\
-$^{3}$Another Department, Different Institution, Street Address, City Postal Code, Country\\
-$^\dagger$NuGrid collaboration}
+%\author[0000-0001-6120-3264]{Pavel Denissenkov}
+$^{1}$Department of Physics and Astronomy, University of Victoria, Victoria, BC, V8W 2Y2, Canada\\
+$^{2}$Joint Institute for Nuclear Astrophysics - Center for the Evolution of the Elements, USA\\
+%\author[0000-0001-8087-9278]{Falk Herwig}
+$^{3}$LCSE and Department of Astronomy, University of Minnesota, Minneapolis, MN 55455, USA\\
+$^{4}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg, Germany\\
+$^\dagger$NuGrid Collaboration, \href{http://nugridstars.org}{http://nugridstars.org}\\}
 
@@
 
-% Enter the current year, for the copyright statements etc.
-\pubyear{2015}
+% Enter the current year, for the copyright statement etc.
+\pubyear{2020}
 
@@
 \begin{abstract}
-This is a simple template for authors to write new MNRAS papers.
-The abstract should briefly describe the aims, methods, and main results of the paper.
-It should be a single paragraph not more than 250 words (200 words for Letters).
-No references should appear in the abstract.
+We present two mixing models for post-processing of 3D hydrodynamic
+simulations applied to convective-reactive \ipr\ nucleosynthesis in a
+rapidly accreting white dwarf (RAWD) with $\mathrm{[Fe/H]} = -2.6$, in
+which H is ingested into a convective He shell during a He flash. A 1D
+advective two-stream model is formulated with physically motivated
+radial and horizontal mixing coefficients constrained by 3D
+hydrodynamic simulations. A more traditional approach uses diffusion
+coefficients calculated from the same simulations. All 3D simulations
+include the energy feedback of the
+\nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} reaction from the
+entrainment of stably stratified H. Global oscillations of shell H
+ingestion in two of the RAWD simulations cause bursts of
+entrainment of H and energy feedback into the flow. With the same
+nuclear network as in the 3D simulations, the 1D advective two-stream
+model reproduces the rate and location of the H burning within the He
+shell closely matching the 3D simulation predictions, as well as
+qualitatively displaying the asymmetry of the $X_{\mathrm{H}}$
+profiles between the up- and downstream. With a full \ipr\ network
+the advective mixing model captures the difference in the n-capture
+nucleosynthesis in the up- and downstream. For example,
+\nuclei{89}{Kr} and \nuclei{90}{Kr} with half-lives of
+\unit{3.18}{\minute} and \unit{32.3}{\second} differ by a factor 2 - 10 in the
+two streams. In this particular application the diffusion approach
+provides globally the same abundance distribution as the advective
+two-stream mixing model. The resulting \ipr\ yields from the diffusive
+and advective post-processing models are compared with observations of
+the exemplary CEMP-r/s star CS31062-050.
+
 \end{abstract}
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3
+convection - hydrodynamics - turbulence - stars: evolution - stars: interiors - stars: white dwarfs - nuclear reactions, nucleosynthesis, abundances.
 \end{keywords}
@@
 
-This is a simple template for authors to write new MNRAS papers.
-See \texttt{mnras\_sample.tex} for a more complex example, and \texttt{mnras\_guide.tex}
-for a full user guide.
+% Herwig 2011, Kippenhahn/MLT, Davis
+The details of mixing in convection zones within the stellar interior
+modifies the evolution of stars from the main sequence to the final
+white dwarf stage or supernova core collapse. The continual mixing of
+H into the convective cores of intermediate and massive stars sets a
+timescale for the eventual main-sequence turn off. This can be
+extended from convective boundary mixing which introduces additional H
+fuel to the core. Through this additional mixing of fuel into
+convection zones convective boundary mixing has a cumulative effect on
+the nuclear-time scale evolution of individual convection zones
+including on the mixture and amount of processed elements, the size of
+the convection zones and thereby on subsequent evolutionary phases
+\citep[for
+  example][]{herwig:00c,Young:2005eg,Denissenkov:2012cu,Battino:2016bna,Davis2019,Wagstaff:2020ce}.
 
-All papers should start with an Introduction section, which sets the work
-in context, cites relevant earlier studies in the field by \citet{1996ApJ...456..902R},
-and describes the problem the authors aim to solve \citep[e.g.][]{cyburt:10}.
+Over the nuclear timescale of the H-burning during the main sequence,
+the mixing of chemical species is computed using either an
+instantaneous or diffusive mixing approximation. The nuclear burning
+timescale is usually significantly longer than the mixing timescale
+within the convective core leading to the details of the mixing within
+the convective zone being sufficiently well modeled with a space-time
+average theory. Such a theory, the mixing length theory
+\citep[MLT][]{cox:68}, describes the energy transport and mixing
+properties of a convective region using averaged quantities over space
+and time.  In advanced stages of stellar evolution the nuclear burning
+timescales approach convective timescales, and so the details of the
+mixing become increasingly important for their structure
+\citep[][]{Herwig2011,Collins:2018cp,Cote:2020bo}.  To quantify this
+phenomenon, it is useful to define the Damk\"ohler number,
+$\mathrm{Da} = \tau_{\mathrm{mix}} / \tau_{\mathrm{nuclear}}$, which
+is the ratio of the mixing and nuclear burning timescales. As this
+number becomes larger and closer to 1, the details of the mixing have
+a greater impact on the burning.
 
-\section{Methods, Observations, Simulations etc.}
+3D hydrodynamic simulations are becoming increasingly accurate in
+capturing the process of entrainment of fuel into a convection zone
+\citep{meakin:07b,Mocak:2011jk,Woodward:2013uf} as well as the
+hydrodynamic feedback resulting from the dynamic nuclear burning of
+the ingested fuel
+\citep{meakin:06a,Herwig:2014cx,Muller:2016kta,Yoshida:2019be,Andrassy:19,Yadav:2020gh}. Such
+simulations predict how species are mixed into the convection zone and
+can determine the convective-reactive nucleosynthesis for a limited
+number of species without needing a post-processing.  However,
+modeling any complicated nucleosynthesis, for example the
+\iprn\ \citep{herwig:11}, or the detailed nucleosynthesis in the
+merger of a O and a C convection shell \citep{Ritter2018} may require
+networks with hundreds or thousands of species that can interact with
+each other, which is well beyond the capabilities of any 3D
+hydrodynamic code running on modern computing clusters. Therefore, 1D
+mixing models are still required to determine any complicated
+nucleosynthesis while 3D hydrodynamic simulations can be used to
+determine the mixing properties of the convection zone and how the
+hydrodynamic instabilities lead to the entrainment of stably
+stratified material. For example, the 3D hydrodynamic simulations of
+\citet{Ritter2018} modeled a convective O shell with a stable C shell
+from a $15\,M_{\odot}$ stellar model of \citet{RitterSE} to obtain
+estimates for the expected entrainment rate of the C-rich
+material. Using diffusive mixing constrained by the mixing properties
+of the convection zone and appropriate entrainment rates, the 1D
+large-network nucleosynthetic post-processing models produced
+significant amounts of odd-Z elements like P, Cl, K and Sc, which
+could explain the underproduction of these elements in current GCE
+models~\citep{Ritter2018}.  The nuclear network used in the 3D
+simulations only included the energy generation from the
+\nuclei{12}{C}$(\nuclei{12}{C},\alpha)$\nuclei{20}{Ne} and subsequent
+\nuclei{16}{O}$(\alpha,\gamma)$\nuclei{20}{Ne} reaction.
 
-Normally the next section describes the techniques the authors used.
-It is frequently split into subsections, such as Section~\ref{sec:maths} below.
+% 
+An interesting case of convective-reactive nucleosynthesis occurs when
+H is ingested into a He burning convective shell.  This triggers the
+\nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} reaction and, after the
+\nuclei{13}{N} beta decays to \nuclei{13}{C}, the
+\nuclei{13}{C}$(\alpha,n)$\nuclei{16}{O} reaction can release neutrons
+if the temperatures within the He shell are high enough. Sakurai's
+object (V4334 Sagittarii) has a unique surface chemical composition
+\citep{asplund:99a} that can be explained with H being ingested into
+the He-shell flash convection zone of this post-AGB
+star~\citep{herwig:11}. This results in the above chain of reactions
+and produces neutron densities high enough to be in the \ipr~regime
+($N_{n} \approx 10^{12} - 10^{16}$\,cm$^{-3}$) \citep{cowan:77}. The
+energy generation from this H ingestion can be significant enough to
+cause a split of the He convective zone in 1D stellar evolution
+models. To study the nucleosynthesis in Sakurai's object,
+\citet{herwig:11} used a spherically symmetric diffusive mixing model
+based on MLT convective velocities, even though in those conditions
+several MLT assumptions are not satisfied. This is shown explicitly in the
+3D hydrodynamic simulations of this very energetic event which bring
+about a global oscillation of shell H ingestion, that causes
+large-scale, non-radial and fast flows \citep{Herwig:2014cx}.
 
-\subsection{Maths}
-\label{sec:maths} % used for referring to this section from elsewhere
+A more quasi-static convective-reactive case of H-ingestion into a He
+shell has been found in the models of rapidly accreting white dwarfs
+(RAWDs) by \cite{Denissenkov:2017ba}. The 3D hydrodynamic simulations
+of \citet{Denissenkov:19} quantified the H-entrainment rates, however
+the diffusive mixing used in the post-processing was taken directly
+from the 1D stellar evolution models. The neutron densities in RAWDs
+reach $N_{n} \approx 10^{14}$\,cm$^{-3}$ resulting in
+\ipr~nucleosynthesis.  The RAWD heavy element production could result
+in a significant contribution of Kr, Rb, Sr, Y, Zr, Nb and Mo to the
+solar composition \citep{Cote2018}. The convective-reactive flows in
+RAWDs are fed by the \nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} energy
+generation that comprises only $2-3\%$ of the total luminosity within
+the He shell which does not lead to a global oscillation of shell H
+ingestion \citep{Denissenkov:19}.
 
-Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
-or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
-as a numbered equation:
+A solution to the concerns about the validity of diffusive mixing in a
+convective-reactive environment and the inability of 3D hydrodynamic
+simulations to simultaneously perform complex nucleosynthesis
+computations is to use a 1D advective mixing model.  One such model
+has been adopted for use in the post-processing nucleosynthesis of
+stellar evolution models from the Monash group, \code{MONSOON}
+\citep{cannon1993, Henkel2017}. The model contains two adjacent
+streams of fluid flow \citep[see our \Fig{elevator} and Fig.~1
+  in][]{Henkel2017}, one with fluid moving upwards and another with
+fluid moving downwards. The two streams have an enforced horizontal
+mixing in order to conserve mass but it can also add in additional
+horizontal mixing. The radial transport velocities as well as the
+additional horizontal mixing within a convection zone are estimated
+with MLT.
 
+A limitation in the two-stream methodology of \code{MONSOON} arises in
+the treatment of the additional horizontal mixing. The strength of
+this mixing has no dependence on the structure of the flow within the
+convection zone. Is the mixing between the two streams that represent
+the dominant dipolar flows of core convection the same as if the flow
+field was at smaller angular scales like in shell
+convection~\citep{chandrabook1961}? There is a dependence on the
+horizontal mixing based on where a cell is within the convection zone
+but shouldn't the mixing between the two streams, in low \mach~number
+flows, be stronger near the convective boundaries where the fluid is
+forced to overturn well before the convective
+boundaries~\citep{Jones:2017kc}? These limitations are addressed in
+the advective mixing model of this work.
+
+In this paper, we describe our adaptation of an advective two-stream
+model for post-processing of detailed 3D hydrodynamic simulations. We
+create 3D hydrodynamic simulations of a RAWD model
+from~\citet{Denissenkov:19} to quantify the mixing of H into the He
+shell and to simulate the global flow including the energy feedback
+from nuclear burning of entrained material. After extracting the
+mixing information from the 3D hydrodynamic simulations for the 1D
+diffusive ~\citep{Jones:2017kc} and advective mixing models, the time
+evolution of the H burning in both of them is calculated.  The details
+of the 3D hydrodynamic simulations, as well as the diffusive and
+advective mixing approaches are outlined in \Section{allmethods}.
+\Section{results} discusses the flow properties of the simulations and shows the post-processing of the 3D hydrodynamic
+simulations with the diffusive and advective mixing routines.
+\Section{conclusions} describes the implications of such results and
+further applications.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Methods}
+\label{sec:allmethods}
+
+\subsection{PPMstar simulations}
+\label{sec:ppmsim}
+
+% Table of runs
+\begin{table*}
+	\centering
+	\caption{Summary of the \ppmstar{} simulations that were computed for this
+          work. The entrainment rates are the slopes of the linear fits shown in
+          \Fig{entrain}, while the different definitions of the convective boundary are
+          discussed in detail in \Sections{convbound}{modelConstraints}.}
+	\label{tab:ppmstarmodels}
+  \begin{threeparttable}
+	\begin{tabular}{ccccccccc} % four columns, alignment for each
+		\toprule
+		Run ID & Grid & $t_{\mathrm{sim}} \unitspace (\mathrm{min})$ & $\langle \tau_{\mathrm{conv}}^{i} \unitspace (\mathrm{min}) \rangle$ & $L_{\mathrm{He}} \unitspace (L_{\odot})$ & $r_{\mathrm{b}, \mathrm{SC}}^{ii} \unitspace (\mathrm{Mm})$ & $r_{\mathrm{b}, v_{\perp}}^{iii} \unitspace (\mathrm{Mm})$ & $\sigma_{r_{\mathrm{b}}, v_{\perp}} \unitspace (\mathrm{Mm})$ & $\dot{M}_{\mathrm{e}}^{iv} \unitspace (M_{\odot} \unitspace \mathrm{s}^{-1})$\\
+		\midrule
+		N15 & $768^{3}$ & 1634 & 19 & $1.46 \times 10^{8}$ & $23.86$ & $23.43$ & $0.48$ & $1.07 \times 10^{-11}$  \\
+		N16 & $1536^{3}$ & 744 & 18 & $1.46 \times 10^{8}$ & $23.84$ & $23.56$ & $0.46$ & $7.21 \times 10^{-12}$  \\
+		N17 & $1152^{3}$ & 631 & 9 & $14.6 \times 10^{8}$ & $26.74$ & $26.69$ & $1.19$ & $1.08 \times 10^{-10}$  \\
+		\bottomrule
+	\end{tabular}
+  \begin{tablenotes}
+    \small
+  \item \textit{Notes}: $^{i}$ The average convective turn over time during the
+    quasi-static phase of each run ($46 < t < 300 \unitspace \mathrm{min}$); $^{ii}$ The
+    initial Schwarzschild boundary as followed in the Lagrangian
+    coordinates at $t = \unit{299}{min}$; $^{iii}$ Boundary where $\partial v_{\perp} / \partial r$ has a
+    minimum at $t = \unit{299}{min}$; $^{iv}$ Entrainment rate of the H-rich 
+    \cldfluid{} 
+  \end{tablenotes}
+  \end{threeparttable}
+
+\end{table*}
+
+The advective and diffusive post-processing methods introduced here are applied
+to 3D hydrodynamic simulations of He-shell flash convection in a rapidly
+accreting white dwarf \citep{Denissenkov:2017ba}. The initial stratification has
+been taken from the stellar evolution model G with the metallicity [Fe/H]\,$= -2.6$
+from \cite{Denissenkov:19}.
+
+As in previous work \citep{Herwig:2014cx,Jones:2017kc} we use the \ppmstar{}
+code of \citet{woodward15} with additional details provided by
+\citet{Andrassy:19}. The explicit Cartesian grid code is based on the
+Piecewise-Parabolic Method \citep[PPM;][]{woodward_colella81,
+woodward_colella84, colella_woodward84, woodward86, woodward07}, and tracks the
+advection of concentrations in a two-fluid scheme using the Piecewise-Parabolic
+Boltzmann method \citep[PPB;][]{woodward86,woodward15}.
+
+The luminosity from the \nuclei{4}{He} burning within the convection zone is
+modeled with a constant volume heating. The entrained H reacts with the abundant
+\nuclei{12}{C} from the triple-$\alpha$ via the
+\nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} reaction. This reaction rate is
+computed using the analytic form of the rate from \citet{angulo:99} with no
+screening factor. We ignore the subsequent beta decay of \nuclei{13}{N} leaving
+a total energy release per reaction of $Q = \unit{1.943}{MeV}$. The stably
+stratified \cldfluid{} contains 89.4\% by
+number of H and the \airfluid{} contains 14.3\% by
+number of \nuclei{12}{C}. The \ppmstar{} simulations done in this work are summarized
+in \Tab{ppmstarmodels}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Diffusive mixing model}
+\label{sec:Dmethod}
+
+\citet{Jones:2017kc} inverted the diffusion equation to derive a
+radius-dependent diffusion coefficient, which produces in 1D the same
+redistribution of species over the time frame of analysis as that given by their
+spherically-averaged 3D simulations of O-shell convection. They measured the
+rate of change in the radius-dependent mass fraction $X(r,\ t)$ of a species by
+computing the difference between the mass fraction profiles at two different
+points in time with some time averaging applied around them. With $\partial X /
+\partial r$ also known from the spherical averages, \citet{Jones:2017kc} solve
+for the unknown diffusion coefficient, which we call $D_{\mathrm{FV}}(r)$, in
+the 1D Eulerian diffusion equation
+%
+\begin{equation*}
+\frac{\partial X}{\partial t} = \frac{\partial}{\partial x}\left( D_{\mathrm{FV}}(r)
+\frac{\partial X(r)}{\partial x} \right),
+\end{equation*}
+%
+where they set $x = r$. We have improved upon this method by mapping
+the results of the input 3D Eulerian simulations to a mass coordinate
+$m(r)$ and inverting the Lagrangian diffusion equation
+%
 \begin{equation}
-    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
-	\label{eq:quadratic}
+\frac{\partial X}{\partial t} = \frac{\partial}{\partial m}\left( \sigma(m)
+\frac{\partial X(m)}{\partial m} \right) + \frac{\dot{q}}{\rho},
+\label{eq:diff-inv-burn}
+\end{equation}
+%
+where $\sigma = (4\pi r^2 \rho)^2 D_\mathrm{FV}(r)$ is the Lagrangian diffusion
+coefficient, and $\dot{q}(m,\ t)$ is the destruction rate of the species by
+nuclear reactions. This new approach has the following advantages. It removes
+the effect of thermal expansion and contraction from $\partial X / \partial t$.
+This effect has negligible influence on the results of~\citet{Jones:2017kc}, but
+it is essential to account for in the expanding convection zone in these RAWD
+simulations. It also properly takes into account the spherical geometry of the
+problem with the radial dependence of the density and species. Included in our
+RAWD simulations but not in the O-shell convection simulations of
+\citet{Jones:2017kc} are nuclear reactions between species of the two distinct
+fluids containing H and \nuclei{12}{C}.
+
+In order to invert \eq{diff-inv-burn} we need to take the difference of two
+averages of the fractional volume profiles, or -- in this case -- the mass
+fraction profile $X(r,\ t)$. For that we estimate the time in which it takes to
+diffuse across one mixing length:
+%
+\begin{equation*}
+\Delta t = \frac{(\alpha_\mathrm{MLT} H_\mathrm{P})^2}{4D_{\mathrm{FV}}}
+\end{equation*}
+%
+where we take $H_\mathrm{P}$ and $D_{\mathrm{FV}}$ at the radius where
+$D_{\mathrm{FV}}$ is at its maximum. This diffusive timescale is $\Delta t
+\approx \unit{2.5}{\minute}$.
+
+\ppmstar{} simulations output a \textit{dump} every several thousand time steps.
+For example in N16 every $\approx 2121$ time steps, where each time step is
+$\approx \unit{\natlog{1.3}{-2}}{\second}$, a single \textit{dump} is output.
+For each \textit{dump} at time $t_\mathrm{D}$, $D_\mathrm{FV}(r)$ is determined
+based on two profiles, $X(r,\ t_\mathrm{D}\pm \Delta t)$, each being averaged
+over $\Delta t$.
+
+Despite taking the burning term into account in \eq{diff-inv-burn}, the profile
+of the entrained material cannot be completely recovered, and thus the method
+cannot provide a diffusion coefficient in the lower part of the convection zone
+where all of the entrained material is burned (top panel \Fig{DvrDVF-compare}).
+%
+\begin{figure}
+  \centering
+	\includegraphics[width=\columnwidth]{figs/N16-DHp-compare-dump650.pdf}
+	\includegraphics[width=\columnwidth]{figs/D-vr-FV-compare.pdf}
+  \caption{Top: $D_\mathrm{vr}$ according to \eq{dvr}, and
+          $D_\mathrm{FV}$ according to the direct determination from the
+          $X_\mathrm{H}$ profiles as well as the pressure scale
+          height at $t = \unit{299}{min}$. Bottom: $D_\mathrm{vr}$ (grey lines) and the composite
+          $D_\mathrm{FV+vr}$ (colour lines) according to the direct
+          determination from the $X_\mathrm{H}$ at various times, merged
+          with $D_\mathrm{vr}$ in the lower part of the convection zone (see
+          text for details). }
+  % Top Fig made in ../notebooks/Diffusion/Lagrangian_diffusion_analysis-make-shell-files.ipynb
+  % Bot Fig made in ../notebooks/Diffusion/D-vr-FV-compare.ipynb
+  \label{fig:DvrDVF-compare}
+\end{figure}
+%
+Therefore we also determine the diffusion coefficient from the
+spherically averaged radial velocity $v_\mathrm{PPM}$ from the 3D
+hydrodynamic simulation using the correction for the near-boundary
+regions recommended by \citet{Jones:2017kc} based on O-shell
+simulations
+%
+\begin{equation}
+D_\mathrm{vr} = \frac{1}{3} v_\mathrm{PPM}\times \min \left(l,|r-r_0|\right),
+\label{eq:dvr}
+\end{equation}
+%
+where $v_\mathrm{PPM}$ is the rms of the radial velocity on spherical shells
+from the 3D \ppmstar\ simulation of the He-shell convection, $l =
+\alpha_{\mathrm{MLT}} H_P$ is the mixing length, and $|r-r_0|$ is the distance
+to the He-shell or another convective boundary that is located at the radius $r_0$. For
+$\alpha_{\mathrm{MLT}} = 1.6$, this prescription provides the best fit to the
+diffusion coefficient derived from the hydrodynamic simulations of O-shell
+convection simulations \citep[see Figure 21 in][]{Jones:2017kc}. However that
+diffusion coefficient recommendation was focused on the behaviour of mixing near
+and across the top convective boundary (CB), and no attempt was made to model
+the discrepancy between the diffusion coefficient determined from the
+spherically averaged 3D hydrodynamic abundance profile evolution and the
+diffusion coefficient determined according to \eq{dvr}. This is clearly seen at
+the middle of the convection zone, $r = \unit{5.5}{Mm}$, in Figure~21 of
+\citet{Jones:2017kc}. In the RAWD case the burning of entrained H-rich material
+takes place approximately in the middle of the convection zone where this
+difference between $D_\mathrm{vr}$ and $D_\mathrm{FV}$ is largest ($\approx 0.4
+\dots \unit{1.2}{dex}$, \Fig{DvrDVF-compare}).
+
+Where we are able to determine $D_\mathrm{FV}$ it is the more accurate diffusion
+coefficient that describes the underlying evolution of the spherically averaged
+3D hydro profiles of these simulations better, for obvious reasons. In order to be able to use this
+more accurate diffusion coefficient we combine it in the lower half with the
+values of $D_\mathrm{vr}$ according to \eq{dvr}. We determine the radius
+$r_\mathrm{Dmax}$ where $D_\mathrm{FV}$ has its maximum. Then
+\begin{equation*}
+  D_\mathrm{FV+vr}= \begin{cases}
+  D_\mathrm{FV}, & \text{if } r > r_\mathrm{Dmax} , \\
+  max(D_\mathrm{FV},D_\mathrm{vr}), & \text{otherwise}.
+\end{cases}
+\end{equation*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Advective mixing model}
+\label{sec:advectmodel}
+
+The 1D advection is formulated using a two-stream approach in which
+one stream transports species radially upwards, while the other stream
+transports them radially
+downwards~\citep[][\Fig{elevator}]{cannon1993, Henkel2017}. Our
+adaptation of this advective two-stream (ATS) model to post-processing
+of 3D hydrodynamic simulations constitutes a reduced-dimensionality
+1.5D advection model.
+
+By default, the two streams are taken to be equal in their surface
+areas which is justified by the analysis of the 3D flow properties
+(see \Section{flow}) and the discussion in
+\Section{radialMix}. The model can have horizontal mixing between up- and
+downstream cells that are adjacent to each other.
+
+There are $N$ cells per stream. The index $i$ refers to the spatial index of the
+$2N$ cells and is used where the equations are agnostic to whether the cell is
+within an up- or downstream. For computational and numerical simplicity, the
+indexing is done such that the downstream is inverted and \textit{stitched} onto
+the top of the upstream. The indexing starts at the bottom of the upstream at
+$i=1$ and so cell $i=N+1$ is at the top of the downstream. The index $k$ refers
+to species.
+
+The discretization distinguishes variables defined on the cell boundaries which
+have spatial half-integer indices, $i+1/2$, while those that represent cell
+averages have spatial integer indices $i$.
+
+\begin{figure}
+
+  \includegraphics[width=0.5\columnwidth]{figs/Advection-Streams.pdf}
+  \centering
+  \caption{An illustration of the two-stream model including all of the fluxes
+          for a cell within the convection zone; $\alpha$ the radial mass flux
+          (\Section{radialMix}), $\beta$ the enforced horizontal mass flux and $\gamma$
+          the additional horizontal mass flux (\Section{horizontalMix}). The index $i$
+          refers to the upstream cell which has an adjacent downstream cell $2N + 1 - i$.}
+  % Fig made in ../notebooks/Methods/Advection-Streams.xcf
+  \label{fig:elevator}
+
+\end{figure}
+
+\subsubsection{Discretized equations}
+\label{sec:discretized}
+
+To formulate the equations we start off with the conservation of mass equation
+and then apply the divergence theorem to it to yield
+%
+\begin{equation}
+  \label{eq:masscons}
+  \partial_{t} \int_{V} \rho \mathrm{d}V = - \oint_{\partial V} \rho \vec{v} \cdot \mathrm{d}\vec{a}
+\end{equation}
+%
+The term on the right hand side is interpreted as a sum of mass fluxes through
+the boundary of the given volume, $V$. The term on the left hand side is the rate of
+change of the mass contained within that volume, $V$. This advective model conserves
+the total mass of every cell which requires that the sum of all mass fluxes at
+every cell is zero. Recasting \eq{masscons} into the partial densities of every
+species, integrating both sides and applying the constraint that the mass of
+every cell is constant at all times leads to
+%
+\begin{equation}
+  \label{eq:fluxes0}
+  \partial_{t} \left( \sum_{k} m_{k,i} \right) = - (\sum_{k}\sum_{j=1}^{5} F_{k,i}^{j}) = 0
+\end{equation}
+%
+where the index $j$ refers to a specific species mass flux on the
+surface of cell $i$. The mass, $m_{k,i}$, of a given species within a
+cell can change however the total mass within that cell cannot. This
+is implicitly satisfied with \eq{fluxes0}. Therefore these equations
+only transport the mass of a given species throughout the convection
+zone. \Eq{fluxes0} includes all fluxes in the advective model and it
+is integrated explicitly.
+
+\subsubsection{Radial mixing and boundary conditions}
+\label{sec:radialMix}
+
+Within the convection zone, the bulk transport of species is through the radial
+direction. The radial mass flux, $\alpha$, on each cell's boundary is given by
+%
+\begin{equation}
+  \label{eq:alpha}
+  \alpha_{i+1/2} = 2 \pi r^{2}_{i+1/2} \rho_{i+1/2} v_{i+1/2}
+\end{equation}
+%
+where $r$, $\rho$, $v$ are the radius, density and velocity defined on
+a cells boundary. The velocity is a positive-definite quantity in this
+model; the species mass fluxes will explicitly carry the appropriate
+sign for transport. In order for this model to remain consistent with
+the nearly-hydrostatic equilibrium of the underlying 3D stellar
+hydrodynamic simulation, the net mass flux at every radius must be
+zero to ensure that there is no net mass transport in the radial
+direction. This means that
+%
+\begin{equation}
+  \label{eq:fluxlayer}
+  \alpha_{i+1/2} = \alpha_{2N+1/2-i}
+\end{equation}
+%
+
+In \eq{alpha}, the radial mass flux depends on a surface area, taken
+to be $2 \pi r^{2}$, to which the underlying transport of mass, $\rho
+v$, is advected through. In principle, the surface area can be
+different between the up- and downstream cells and still ensure that
+the net mass flux is zero so long as the product $\rho v$ with the
+respective surface areas are constant at every radius.  With the low
+\mach~number flows in the RAWD simulations, the largest density
+perturbations are at the percent level as seen in \Fig{mollweide}. The
+density can therefore be approximated to be constant at every radius
+so that $\rho_{i+1/2} = \rho_{2N+1/2-i}$. The spherical average of the
+radial velocity at every radius is approximately zero
+(\Fig{mollweide}). The magnitude of the velocity at the surface of the
+up- and downstream cells at each radius can then be approximated as
+being the same, $v_{i+1/2} = v_{2N+1/2-i}$. With the density and
+velocities being equal in both streams at a given radius, the surface
+areas of each stream must also be equal to ensure that there is no net
+radial mass transport. Another consequence of these approximations is
+that the mass of the cells in both streams at a given radius are also
+equal, $\delta m_{i} = \delta m_{2N+1-i}$.
+
+The radial species mass fluxes for cell $i$ are
+%
+\begin{subequations}
+\label{eq:Rfluxes}
+\begin{align}
+  F_{k,i}^{O} &= \alpha_{i+1/2} X_{k,i+1/2} \\
+  F_{k,i}^{I} &= -\alpha_{i-1/2} X_{k,i-1/2}
+\end{align}
+\end{subequations}
+%
+where the superscript $O$ and $I$ refer to the outflow and inflow of mass at
+cell $i$, respectively. These constitute two of the fluxes from \eq{fluxes0}.
+The mass fractions, which are defined in the center of a cell, $X_{k,i}$, are
+considered the average within that cell. To
+achieve second order accuracy in the solutions of these equations, the mass
+fraction on a boundary, $X_{k,i+1/2}$, is determined through a linear
+interpolation using the neighbouring cell averages. There are
+two estimates for the interpolated state,
+%
+\begin{subequations}
+\begin{align*}
+  X_{k,i+1/2} &= X_{k,i+1} - \frac{1}{2}\frac{\partial X_{k,i+1}}{\partial m_{i+1}}\delta m_{i+1} \\
+  X_{k,i+1/2} &= X_{k,i} + \frac{1}{2}\frac{\partial X_{k,i}}{\partial m_{i}}\delta m_{i} 
+\end{align*}
+\end{subequations}
+%
+referring to the \textit{up-sided} and \textit{down-sided} estimates of the
+interpolated mass fraction, respectively. To ensure that the numerical scheme is
+stable, the interpolated state is chosen such that the discretization is
+\textit{upwinding}. In practice, this just means that if the velocity is
+upwards, the \textit{upwinded} interpolated state is the \textit{down-sided}
+estimate because material is being advected upwards. To reduce oscillations in
+the solutions the minmod limiter is used on the numerically estimated slope
+\citep{LeVeque2002FiniteVM}.
+%
+\begin{equation*}
+  \frac{\partial X_{k,i}}{\partial m_{i}} = \code{minmod}(\frac{X_{k,i} - X_{k,i-1}}{\delta m_{i}}, \frac{X_{k,i+1} - X_{k,i}}{\delta m_{i}})
+\end{equation*}
+%
+where 
+\begin{align*}
+  \code{minmod}(a,b) = \left\{
+  \begin{array}{lr}
+      a & \text{if } |a| < |b| \text{ and } a \cdot b > 0 \\
+      b & \text{if } |b| < |a| \text{ and } a \cdot b > 0 \\
+      0 & \text{otherwise}
+  \end{array}
+  \right.
+\end{align*}
+
+At the inner and outer boundaries of the convection zone the velocities are
+zero. Physically, this condition is enforcing that all of the radial flow is
+turning over at the boundary such that there is only a horizontal flow. Of
+course, fluid can and does over turn at some distance before the
+boundary~\citep{Jones:2017kc} which are written as sources of horizontal mixing
+in this model (\Section{horizontalMix}). The constraints on the radial mass flux
+coefficients to enforce a horizontal flow at the boundaries are
+%
+\begin{subequations}
+\begin{align*}
+  &\alpha_{N-1/2} = \alpha_{N+1/2} = \alpha_{N+3/2} \\
+  &\alpha_{2N-1/2} = \left( \alpha_{2N+1/2} \equiv \alpha_{1/2} \right) = \alpha_{3/2}
+\end{align*}
+\end{subequations}
+%
+These coefficients cause, at the uppermost cell in the upstream, all of the mass
+that enters that cell to flow directly into the uppermost cell in the
+downstream. This is a horizontal flow. These boundary conditions are essentially
+periodic boundary conditions and from the numerical and computational
+perspective, it is convenient to have the two streams attached to each other to
+form a ring. By applying \eq{masscons} to a convection zone that has zero
+velocity on its boundaries, there is no mass entering or leaving the convection
+zone and so it remains constant. For this reason, the model follows the
+Lagrangian coordinates of the \ppmstar{} initialized convection zone as it
+expands in Eulerian coordinates (\Section{convbound}).
+
+\subsubsection{Horizontal mixing}
+\label{sec:horizontalMix}
+
+With only the radial mass fluxes given by \eq{Rfluxes} contributing to
+\eq{fluxes0} thus far, the only way in which the fluxes at the upper and lower
+boundary of any cell sum to zero is if the product of $2 \pi r^{2} \rho v$ is
+constant for all radii. This is not true for the convection zone in the RAWD
+simulations nor in general. Rather, the rms radial velocity
+profile from the 3D simulations in \Fig{rprofs} shows a pronounced peak about
+1/3$^\mathrm{rd}$ from the bottom of the convection zone and falls off well
+inside the CBs where the flow turns around in a broad sweep corresponding to
+the low \mach~numbers.
+
+Using \Fig{elevator} as a reference, if the upstream has $\alpha_{i+1/2} >
+\alpha_{i-1/2}$, then over a time step the mass within that cell $i$ will
+decrease. Simultaneously the downstream will be increasing its mass by the same
+amount due to the radial mass fluxes being equal in the two streams at every
+radius (\eq{fluxlayer}). To conserve the mass in each of the cells, there is an
+enforced horizontal mass flux of
+%
+\begin{equation}
+  \label{eq:beta}
+    \beta_{i} = \alpha_{i+1/2} - \alpha_{i-1/2}
+\end{equation}
+%
+from one stream to the other. The sign of this coefficient $\beta$ determines
+whether mass is transferred from the downstream to the upstream or vice versa.
+The horizontal species mass flux at the upstream cell with index $i$ is
+%
+\begin{align*}
+  F^{\beta}_{k,i} = \left\{
+  \begin{array}{lr}
+      - | \beta_{i} | X_{k,2N+1-i} & \text{if } \beta_{i} > 0 \\
+       | \beta_{i} | X_{k,i} & \text{if } \beta_{i} < 0
+  \end{array}
+  \right.
+\end{align*}
+%
+
+One could consider a situation where neighboring cells at the same radius
+conserve mass in the shell but allow for the mass in each cell to be variable so
+that the $\beta$ coefficient is not exactly as written in \eq{beta}. However,
+since the density fluctuations are at the percent level as shown in
+\Fig{mollweide} they are approximated as being the same between the two streams at every radius.
+Therefore the mass within each cell should not change due to horizontal mixing.
+Combining this fact with there being no net radial transport of mass, the mass
+within every cell is constant at all times.
+
+With the $\beta$ and $\alpha$ mass fluxes, the total mass flux at every cell is
+zero. There can be additional horizontal mass fluxes so long as the sum of them
+is equal to zero. This additional horizontal mass flux is given the symbol
+$\gamma$ and it is unique within each shell, i.e $\gamma_{i} =
+\gamma_{2N+1-i}$, to ensure that the total mass flux at every cell is still
+zero. However, the additional horizontal species mass flux is not zero and has
+the form
+%
+\begin{equation}
+\label{eq:gammaflux}
+  F^{\gamma}_{k,i} = \gamma_{i} \left( X_{k,i} - X_{k,2N+1-i} \right)
+\end{equation}
+%
+for each cell.
+
+While mass is being transported radially in the up- and downstreams, mass is
+also being exchanged between them through a horizontal mass flux. The mixing of
+the mass of a given species $k$ between cell $i$ and its adjacent cell $2N+1-i$
+implied by \eq{gammaflux} has the effect of homogenizing the species between the
+two streams at every layer, depending on the value of $\gamma$. There are two
+competing timescales that determine how efficient the mixing between the up- and
+downstreams are. These are the radial advection timescale,
+%
+\begin{equation}
+  \label{eq:radialT}
+  \delta t_{r,i} = \frac{|\delta r_{i}|}{v_{r,i}}
+\end{equation}
+% 
+and the horizontal time scale, $\delta t_{h,i}$, for a given cell. Associated
+with these timescales are mass fluxes. The radial mass flux is $\alpha$, while
+the horizontal mass flux is $\gamma$. With these two competing timescales, if
+one is shorter than the other then it is implied that the shorter timescale has
+a larger mass flux than the longer timescale. This can be written as
+%
+\begin{equation}
+  \label{eq:timescales}
+  \gamma_{i} = \alpha_{i} \frac{\delta t_{r,i}}{\delta t_{h,i}}
+\end{equation}
+%
+
+The mental picture of a convection zone being composed of one upstream and one
+downstream that splits the convection zone evenly into two hemispheres is very
+unrealistic (\Fig{mollweide}). Instead, this model should be thought of as the
+upstream being the superposition of all radially upward flows and similarly for
+the downstream. From this idea, if the upward flows are small in their surface
+area at a given radius, they can more easily mix with the adjacent downward
+flows. To decompose the velocity into upward and downward flows at a particular
+length scale on a sphere, the power spectrum (spherical harmonics) of the radial
+velocity is taken. To compute the spherical harmonics the python package
+\code{pyshtools} is used for data sampled on a sphere. The maximum mode, $\ell$,
+that the velocity field is decomposed into is chosen such that the smallest
+wavelength, $\lambda = 2 \delta r$ where $\lambda = 2 \pi r / \sqrt{\ell(\ell +
+1)}$, that can be sampled from the \textit{briquette} data (see \Fig{mollweide}
+and
+\Section{RAWD_Hydro}) with a grid spacing of $\delta r$ is computed.
+
+For a given mode, $\ell$, there is an associated length scale, or wavelength. A
+particle at the center of a stream must move, tangentially to the surface of the
+sphere, half of this wavelength to be in the center of the adjacent stream. With
+an average tangential velocity, the particle will take $\delta t_{h,i,\ell} =
+\pi r_{i} / \left( \langle|v_{\perp,i}|\rangle\sqrt{\ell(\ell+1)} \right)$
+amount of time to mix, for a given mode $\ell$. The flow does not develop with
+only one very dominant mode but a spectrum of modes (\Fig{power-spectrum}) and
+so the horizontal timescale is weighted by its power, $S_{cc}(\ell,r) =
+\sum_{m=-\ell}^{\ell}|c_{\ell,m}(r)|^{2}$. Therefore, the horizontal timescale
+is
+%
+\begin{equation}
+  \label{eq:horizontalT}
+  \delta t_{h,i} = \sum_{\ell} \frac{S_{cc}(\ell,r_{i}) \pi r_{i}}{\left( \sum\limits_{\ell} S_{cc}(\ell,r_{i}) \right) \langle |v_{\perp,i}| \rangle\sqrt{\ell(\ell+1)}}
 \end{equation}
 
-Refer back to them as e.g. equation~(\ref{eq:quadratic}).
+\subsubsection{Entrainment}
+\label{sec:entrain}
 
-\subsection{Figures and tables}
+A convection zone can entrain, or ingest, material due to hydrodynamic
+instabilities at the boundaries. In the RAWD simulations, the \cldfluid{} 
+is entrained into the convection zone through a downstream at the convective
+boundaries, as shown in \Fig{mollweide}, bringing H-rich material into the
+convection zone. With the constraint on the advective model that the mass within
+any cell cannot change, the mass of the \cldfluid{} that is entrained into
+a cell must also be removed. Algorithmically, the entrainment process follows
+what was discussed in detail in Appendix A of \citet{Denissenkov:19}. The H-rich
+material is ingested into the downstream into a region of mass, $\Delta M$, that
+is equal to the mass of the top cell of the downstream. This ensures that all of
+the mass that is entrained is done so directly through the convective boundary
+surface, thus incorporating the horizontal and radial mixing timescales to
+determine how fast the composition changes are transported downwards. Due to
+$\Delta M$ being only one cell, the change in the mass fractions is applied as a
+step increase.
 
-Figures and tables should be placed at logical positions in the text. Don't
-worry about the exact layout, which will be handled by the publishers.
+To test how well entrainment and mixing is modeled we have switched off
+all reactions and compared the total amount of H ingested into the top cell with
+the amount of H distributed over the other cells by mixing. The relative
+difference between these amounts in the advective model remains within $2-4\%$
+even after 30334 time steps (\unit{744}{min} of integration time). In the
+diffusive model the entrained material is distributed evenly over 18 cells (out
+of a total number of 256 cells) using the step increase method from Appendix A
+of \citet{Denissenkov:19}. Over the same number of time steps as the advective
+model we find that the relative differences between the total entrained H and
+the mixed H in the diffusive model to be of the same order, $2-4\%$.
 
-An example figure can be seen in \Fig{mass-N14}.
-, and tables as
-e.g. \Tab{example_table}.
+\subsubsection{The Courant Condition}
+\label{sec:courant}
 
-% Example figure
+With the fact that the method is explicit, the time steps are limited by the
+Courant condition. With the cells being discretized in mass, the Courant
+condition can be plainly stated as requiring that the total amount of mass
+advected out of any given cell in a single time step cannot be larger than the
+mass within that cell. The Courant number in any cell is given by
+%
+\begin{equation}
+  \label{eq:courant}
+  C_{i} = \frac{\delta t \left(\alpha_{i+1/2} + \gamma_{i} + |\beta_{i}| \right)}{\delta m_{i}}
+\end{equation}
+%
+and the Courant condition states that for all $i$, $C_{i} \leq 1$. Any advective
+post-processing simulations have the condition that the maximum Courant number
+across all cells is $0.5$. This determines the time steps that any
+post-processing model takes (see \Section{modelConstraints}).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\mppnp{} post-processing simulations}
+\label{sec:mppnpSims}
+
+The 1D multi-zone NuGrid code, \mppnp{}
+\citep{Pignatari:2016er,RitterSE}, is used for the 1D post-processing
+models of the \ppmstar{} simulations. Either the diffusive or
+advective mixing routine, as described in
+\Sections{Dmethod}{advectmodel} respectively, is used for a given
+\mppnp{} simulation which are tabulated in \Tab{mppnp_runs}. The first
+set of runs has been performed by including only the
+$\nuclei{12}{C}(\proton,\gamma)\nuclei{13}{N}$ reaction rate and
+neglecting its electron screening, just as in the \ppmstar{} runs, in
+order to have a direct comparison between 1D and 3D. The second set of
+runs has been performed with a full network of $\sim$1000 species
+suitable for \ipr\ simulations in which we use the same nuclear data
+and electron screening factors as in \citet{Denissenkov:19}. Both the
+advective and diffusive mixing post-processing models, for a given 3D
+\ppmstar{} run, use the same spherically averaged radial $\rho$, $T$
+profiles and time steps corresponding to the 3D dump times. The
+details of the formulation of the models are discussed
+in \Section{modelConstraints}.
+
+\begin{table}
+  \centering
+  \caption{Summary of the 1D \mppnp{} post-processing simulations.}
+	\label{tab:mppnp_runs}
+
+  % make sure it is a column
+  \resizebox{\columnwidth}{!}{%
+
+  \begin{threeparttable}
+    \begin{tabular}{llll} % four columns, alignment for each                              
+      \toprule
+      \mppnp{} Run ID & A/D$^i$            & Hydro Run ID & Network$^{ii}$ \\
+      \midrule
+      mp1             & $D_\mathrm{FV+vr}$ & N16          & $\nuclei{12}{C}(\proton,\gamma)\nuclei{13}{N}$\\
+      mp2             & ATS               & N16          & $\nuclei{12}{C}(\proton,\gamma)\nuclei{13}{N}$\\ 
+      mp3             & $D_\mathrm{vr}$    & N17          & $\nuclei{12}{C}(\proton,\gamma)\nuclei{13}{N}$\\
+      mp4             & ATS               & N17          & $\nuclei{12}{C}(\proton,\gamma)\nuclei{13}{N}$\\ 
+      mp5             & $D_\mathrm{FV+vr}$ & N16          & full\\ 
+      mp6             & ATS               & N16          & full\\ 
+      mp7             & $D_{\mathrm{vr}}$  & N17          & full\\ 
+      mp8             & ATS               & N17          & full\\ 
+      mp9             & $D_{\mathrm{vr}}$  & N16          & $\nuclei{12}{C}(\proton,\gamma)\nuclei{13}{N}$\\
+      mp10            & $D_{\mathrm{vr}}$  & N16          & full\\
+      \bottomrule
+    \end{tabular}
+  \begin{tablenotes}
+    \small
+    \item $^i$ The mixing model used in the post-processing which is either
+          diffusive ($D_{\mathrm{vr}}$ or $D_{\mathrm{FV+vr}}$, \Section{Dmethod}) or
+          advective (ATS, \Section{advectmodel}); $^{ii}$ $\nuclei{12}{C}(\proton,\gamma)\nuclei{13}{N}$
+          indicates post-processing with the same one-reaction burn that is implemented in
+          the \ppmstar{} runs, full indicates post-processing with the complete network
+          needed for \ipr{} modeling
+  \end{tablenotes}
+\end{threeparttable}
+}
+\end{table}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+\label{sec:results}
+
+We first describe the hydrodynamic simulations of RAWDs in \Section{RAWD_Hydro}.
+The details of the post-processing models are discussed in \Section{modelConstraints}.
+Focusing on the only nuclear reaction included in the hydrodynamic simulation we
+then describe and compare post-processing via the diffusive (\Section{Dc12pg})
+and advective methods (\Section{Advc12pg}). In \Section{fulllnetworkresults} we
+describe the post-processing results including a full network and comparison
+with observations.
+
+\subsection{3D hydrodynamic simulations of RAWDs}
+\label{sec:RAWD_Hydro}
+\subsubsection{Flow properties}
+\label{sec:flow}
+
+As with the other \ppmstar{} simulations in
+\citet{woodward15,Jones:2017kc,Andrassy:19}, the RAWD simulations do not
+start with any initial perturbations in the velocity field but rather the
+numerical representation of the spherically symmetric thermodynamic variables
+develop instabilities. These are quickly over taken by the flow developing from
+heat being injected (\Tab{ppmstarmodels}) in a thick spherical shell. This shell
+is contained within the radii $\unit{8.28}{Mm}$ and $\unit{10.28}{Mm}$ and can
+be seen as the beige shaded region in \Fig{rprofs}. After about 30 minutes this
+transient state is completely lost in the simulations and the natural flow of
+the convection zone has developed.
+
 \begin{figure}
-  % To include a figure from a file named example.*
-  % Allowable file formats are eps or ps if compiling using latex
-  % or pdf, png, jpg if compiling using pdflatex
+  \includegraphics[width=\columnwidth]{figs/vrprofs.pdf}
+  \centering
+  \caption{The rms radial profiles of $v_{r}$, $v_{\perp}$ and
+          $v$ at $t = \unit{299}{min}$. The thick lines are from run \code{N16}, while
+          the thin lines are from run \code{N15}. The black dotted lines correspond to the
+          convective boundaries that are used in \code{N16}'s post-processing models
+          (\Sections{convbound}{modelConstraints}). The beige shaded region is where the
+          volume heating is applied. When spatially integrated it corresponds to the
+          helium luminosity, $L_{\mathrm{He}}$, stated in \Tab{ppmstarmodels}.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:rprofs}
 
-  %\includegraphics[width=\columnwidth]{figs/figure_template/mass-N14}
-  \caption{This is an example figure. Captions appear below each
-    figure.  Give enough detail for the reader to understand what
-    they're looking at, but leave detailed discussion to the main body
-    of the text.  This particular figure file will appear when you
-    exectute the example notebook in
-    \texttt{figs/figure\_template}. Then uncomment the
-    \texttt{includegraphics} command in the latex source file.} 
-    \lFig{mass-N14}
 \end{figure}
 
-Another results is also good \Fig{mass-O16}.
-% Example table
-\begin{table}
+\begin{figure*}
+
+  \begin{minipage}{.49\textwidth}
     \centering
-	\caption{This is an example table. Captions appear above each table.
-	Remember to define the quantities, symbols and units used.}
-	\lTab{example_table}
-	\begin{tabular}{lccr} % four columns, alignment for each
-		\hline
-		A & B & C & D\\
-		\hline
-		1 & 2 & 3 & 4\\
-		2 & 4 & 6 & 8\\
-		3 & 5 & 7 & 9\\
-		\hline
-	\end{tabular}
-\end{table}
+    \includegraphics[width=\textwidth]{figs/N16-rho-mollweide-low.pdf}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/N16-rho-mollweide-high.pdf}
+  \end{minipage} \\
 
-% Example figure
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/N16-vr-mollweide-low.pdf}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/N16-vr-mollweide-high.pdf}
+  \end{minipage} \\
+
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/N16-XH-mollweide-low.pdf}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/N16-XH-mollweide-high.pdf}
+  \end{minipage}
+
+  \caption{In each row the left panel is a Mollweide plot of the quantity at a
+          radius of $\unit{14.5}{Mm}$, which is within the H burning region
+          (\Fig{burningrate}), while the right panel is at a radius of $\unit{23}{Mm}$
+          which is near the top CB (\Tab{ppmstarmodels}). The first row plots the density
+          perturbations from its mean, the second row plots the radial velocity, while the
+          last row plots the mass fraction of H which is calculated from the FV that is at
+          double the grid resolution. The Mollweide plots were made with the
+          \textit{briquette} data which is downsampled by a factor of 4 (384$^{3}$) from
+          the resolution of the underlying run, \code{N16} (1536$^{3}$), and are taken at
+          $t = \unit{299}{min}$. The points on the shell to which the quantity is sampled
+          on are distributed such that each point's surface area coverage is roughly equal
+          to $4 \pi / N$. The number of points that are used roughly corresponds to having
+          a single point per cubic cell.}
+  % Figs made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:mollweide}
+
+\end{figure*}
+
+The rms radial profiles of the radial and tangential velocities are shown in
+\Fig{rprofs}. The radial velocity drops sharply near the CBs, while the
+tangential velocity is dominant near the CBs. Directly from these profiles it
+is clear that there will be significantly more horizontal mass transport near
+the CBs (\eq{timescales}) than the middle of the convection zone. This
+coincides with the flows being forced to turn over near the CBs. \code{N15}'s
+spherically averaged velocities are smaller than \code{N16}'s and it is
+significant when considering that the difference between the two runs is the
+doubling of the spatial resolution in \code{N16}. A possible cause for this is
+due to the higher entrainment rates in \code{N15} compared to \code{N16}, shown
+in \Fig{entrain}. With the convective fluids doing work to bring the initially
+stable \cldfluid{} into the convection zone, some of its kinetic energy is
+lost resulting in the lower velocities.
+
+\begin{figure*}
+
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/N15-vrspectra.pdf}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/N16-vrspectra.pdf}
+  \end{minipage}
+  \caption{The power spectrum, in terms of the spherical harmonic modes, $\ell$,
+          of the radial velocity as a function of radius at $t = \unit{299}{min}$ within
+          the convection zone. The left panel is from run \code{N15}, while the right panel
+          is from run \code{N16}. The power in each radial bin is normalized by the
+          maximum power within that radial bin.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:power-spectrum}
+
+\end{figure*}
+
 \begin{figure}
-	% To include a figure from a file named example.*
-	% Allowable file formats are eps or ps if compiling using latex
-	% or pdf, png, jpg if compiling using pdflatex
-	\includegraphics[width=\columnwidth]{figs/figure_template/mass-O16}
-    \caption{Another figure.}
-    \lFig{mass-O16}
+
+  \includegraphics[width=\columnwidth]{figs/lspectrum.pdf}
+  \centering
+  \caption{The power spectrum of the radial velocity as a function of the spherical harmonic mode,
+          $\ell$, at select radii at $t = \unit{299}{min}$. The
+          thick lines are run \code{N16}, while the thin lines are from run \code{N15}. The
+          spectrum is limited by the Nyquist sampling of the \textit{briquette} data
+          resulting in more $\ell$ modes being resolved in the higher resolution run,
+          \code{N16}. The power in each spectrum at a given radius is scaled by an
+          arbitrary constant factor, which is the same for each hydro run, in
+          order to show their $\ell$ dependence clearly.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:lspectrum}
+
 \end{figure}
 
-\section{Conclusions}
+The radial velocity field is shown at two radii in \Fig{mollweide}. These
+Mollweide-projection plots are made using the \textit{briquette} data from a
+\ppmstar{} simulation. This data set is downsampled in each spatial direction by
+a factor of four from the original simulation through averaging the data in
+4$^{3}$ cells. The radial velocity at $\unit{14.5}{Mm}$ is mostly dominated by
+two modes, $\ell = 2$ and $3$, which can be seen visually in \Fig{mollweide} as
+well as from its power spectrum in \FigTwo{power-spectrum}{lspectrum}. This is
+consistent with the flow being dominated by the most unstable and largest
+convective mode that can be in that spherical shell, $\ell \approx \pi r /
+\Delta r \approx 3$~\citep{chandrabook1961}. At $\unit{23}{Mm}$, the velocity
+field is not dominated by a few modes but the power is instead spread over many
+modes of $\ell$. The large plumes that are advecting from the center of the
+convection zone are broken up into smaller, incoherent streams that are swept
+across by the large tangential velocities (\FigTwo{rprofs}{vt-mollweide}).
 
-The last numbered section should briefly summarise what has been done, and describe
-the final conclusions which the authors draw from their work.
+\begin{figure*}
+
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/n16-vt-mollweide-low.pdf}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{figs/n16-vt-mollweide-high.pdf}
+  \end{minipage}
+  \caption{The magnitude of the tangential velocity, $|v_{\perp}| =
+          \sqrt{v_{\phi}^{2} + v_{\theta}^{2}}$, on spherical shells from \code{N16}.
+          The left panel is at a radius of $\unit{14.5}{Mm}$, within the H burning region
+          (\Fig{burningrate}), while the right panel is at a radius of $\unit{23}{Mm}$
+          which is near the upper convective boundary (\Tab{ppmstarmodels}). These
+          snapshots are taken at $t = \unit{299}{min}$.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:vt-mollweide}
+
+\end{figure*}
+
+\subsubsection{The convective boundary and entrainment and burning of H}
+\label{sec:convbound}
+
+The CB in 1D stellar evolution models can be determined by the Schwarzschild
+criterion. If the fluid is unstable to convection and is fully mixed within the
+convection zone, it is adiabatically stratified such that $dS/dr = 0$, or in the
+case of an ideal gas equation state, which is used for the simulations done in
+this paper, it can be expressed as $dA/dr = 0$ where $A = P / \rho^{\gamma}$
+with $\gamma = 5/3$. The \ppmstar{} simulations are initialized with a
+convection zone defined by these properties. The CB can be determined throughout
+the entirety of the simulation by assuming that the convection zone is only
+expanding due to heat and so it can be determined directly by using the
+Lagrangian coordinates of the initial Schwarzschild boundary. This initial
+Schwarzschild boundary is determined numerically with the condition that fluid
+with $dA/dr > 0$ is stably stratified. In previous works that used the \ppmstar{}
+code \citep{Jones:2017kc, Andrassy:19,Denissenkov:19} the CB during the
+simulation was determined using the minimum of $\partial v_{\perp} / \partial r$
+with the spherically averaged profiles of $|v_{\perp}|$ or with the
+\textit{bucket} data of $v_{\perp}$ (see Section~3.3 in \citet{Jones:2017kc}).
+The Schwarzschild criterion does not adequately describe the stability of the
+fluid near the boundaries in these simulations as even in areas where the
+entropy gradient is weakly positive, the fluid is flowing with moderate
+velocities \citep{Jones:2017kc}. The gradient condition expresses the 3D nature
+of the CB as when the fluid advects near the stiff boundary, the fluid is forced
+to turn over. This can be viewed as small perturbations from a spherically
+symmetric boundary as shown in \Fig{vtbound}. The thickness of this CB as
+described by 1$\sigma$ spatial fluctuations~\citep[Fig.~17 in][]{Jones:2017kc}
+is approximately $\unit{0.5}{Mm}$, which is smaller than the pressure scale
+height at that boundary, $H_{P} = \unit{1.0}{Mm}$. The CB as determined by the
+minimum of $\partial v_{\perp} / \partial r$ as well as the CB defined by the
+Lagrangian coordinates of the initial Schwarzschild boundary for all runs at $t
+= \unit{299}{min}$ are tabulated in \Tab{ppmstarmodels}. A discussion on the
+appropriate boundary for the \mppnp{} post-processing models is
+within \Section{modelConstraints}.
+
+\begin{figure}
+
+  \includegraphics[width=\columnwidth]{figs/N16-vt-boundary.pdf}
+  \centering
+  \caption{Location of the upper convective boundary of \code{N16} according to
+          the minimum of $\partial v_{\perp} / \partial r$ at $t = \unit{299}{min}$ from
+          the \textit{briquette} data. Taking the spherical average, the upper convective
+          boundary is at $\unit{23.56}{Mm}$ with $\sigma_{r_{\mathrm{b}},
+            v_{\perp}} = \unit{0.46}{Mm}$. This is consistent with the other CB
+          determination which uses the mass coordinates of the initial Schwarzschild
+          boundary to yield an upper CB at $\unit{23.84}{Mm}$.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:vtbound}
+
+\end{figure}
+
+\begin{figure}
+
+    \includegraphics[width=\columnwidth]{figs/N15-entrainment.pdf}
+    \includegraphics[width=\columnwidth]{figs/N16-entrainment.pdf}
+    \includegraphics[width=\columnwidth]{figs/N17-entrainment.pdf}
+
+  \centering
+  \caption{The time evolution of the mass of the \cldfluid{} being
+          entrained and burned within the convection zone since the start of the \mppnp{}
+          post-processing models, $t = \unit{46}{min}$. The top panel is from \code{N15},
+          the middle panel is from \code{N16} and the bottom panel is from \code{N17}. The
+          total lines is the instantaneous entrainment rate of the \cldfluid{} which
+          is used in all advective and diffusive post-processing models. A linear fit of
+          the entrainment rates, $\dot{M}_{\mathrm{e}}$, for each run is calculated over a
+          quasi-static time interval corresponding to the solid line, while the dotted line
+          is an extension of that fit. The black vertical line is at $t = \unit{501}{min}$
+          when the images of \Fig{renderings} were rendered.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:entrain}
+
+\end{figure}
+
+At the upper CB, the entrained \cldfluid{} follows the convective
+downflows deep into the convection zone until it reaches the burning region
+where the \nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} reaction occurs. To
+determine the entrainment rates of \code{N15}, \code{N16} and \code{N17}, a
+method, which is described in more detail in \citet{Andrassy:19} and
+\citet{Denissenkov:19}, was used. To summarize, the total mass of the
+\cldfluid{} that was entrained is composed of the mass that has been
+burned and the mass that is present within the convection zone with an upper
+boundary radius of $r_\mathrm{ub}$. To determine the mass of the \cldfluid{}
+within this convection zone its density is integrated to within
+\unit{0.5}{Mm} of the formal CB of the \mppnp{} post-processing simulations
+(see \Section{modelConstraints}). This offset is approximately the average scale
+height of the rms tangential velocity gradient at the boundary, $H_{v_{\perp},
+\mathrm{ub}} = (\partial \: \mathrm{ln} \: v_{\perp} / \partial r)^{-1}$, a
+condition used in \citet{Jones:2017kc}, \citet{Andrassy:19}, and
+\citet{Denissenkov:19}, for all RAWD simulations during their quasi-static
+burning phases. The constant offset prevents major fluctuations in the
+calculated entrained mass due to the very large concentrations of the
+\cldfluid{} near the CB and prevents major changes in the velocity field
+(global oscillation of shell H ingestion in \code{N15} and \code{N17}; see \Section{goshruns}) from providing
+outlandish integration boundaries. This offset is extended to \unit{5}{Mm} for
+\code{N17} during its global oscillation of shell H ingestion due to the major changes in the spherically averaged
+\cldfluid{} concentrations near the majorly perturbed convective boundary. The
+burnt material is calculated using the spherical profiles of density,
+temperature and mass fraction to determine what the burning rate per unit volume
+is. This burning rate is integrated in time to determine the amount burnt over a
+\textit{dump}. The entrainment rates, mass burnt, and present material of the
+\cldfluid{} within the CBs of \code{N15}, \code{N16} and \code{N17} are
+shown in \Fig{entrain}. A linear fit of the entrainment rate of \code{N15},
+\code{N16}, and \code{N17} over their quasi-static burning phases are
+$\dot{M}_{\mathrm{e}} = 1.06 \times 10^{-11}\,M_{\odot}$\,s$^{-1}$,
+$\dot{M}_{\mathrm{e}} = 7.21 \times 10^{-12}\,M_{\odot}$\,s$^{-1}$, and
+$\dot{M}_{\mathrm{e}} = 1.08 \times 10^{-10}\,M_{\odot}$\,s$^{-1}$,
+respectively. \code{N15} and \code{N17}'s entrainment rates become non-linear
+and increases significantly around $t = \unit{300}{min}$ (\Fig{goshrprofs}).
+Even within the linear regime the entrainment rate of \code{N15} is $\approx
+10\%$ larger than \code{N16}'s though the scale of this difference is consistent
+with the entrainment convergence results in Fig.~17 of \citet[][]{woodward15}.
+
+Throughout the entirety of the \code{N16} simulation, the burning and
+entrainment of H maintains a quasi-static state resulting in the linear
+growth of the total entrained material. The distribution of $X_{\mathrm{H}}$ is
+plotted on spherical shells near the upper CB, \unit{23}{Mm}, and well within
+the H burning region, \unit{14.5}{Mm}, in \Fig{mollweide}. The corresponding
+radial velocity field at those radii is shown in \Fig{mollweide}. The
+distribution of the $X_{\mathrm{H}}$ at \unit{14.5}{Mm} in conjunction with the
+radial velocity distribution shows that that the upflows are essentially H-free
+while the downflows are H-rich. As the H-rich material moves through the H
+burning region, the downflow material is rapidly burned until it is H-free.
+Eventually this material will turn around and move in the upflows entirely
+H-free. The H-free material is advected and mixed with the H-rich material as it
+is advected towards the upper boundary where it still maintains very small mass
+fractions ($X_{\mathrm{H}} \approx 10^{-6}$) at \unit{23}{Mm}, $\approx
+\unit{0.8}{Mm}$ from the upper CB (\Tab{ppmstarmodels}). The H-rich material
+($X_{\mathrm{H}} \approx 10^{-3}$) is advected into the convection zone in the
+downflows near the CB.
+
+\subsubsection{A global oscillation of shell H ingestion in \code{N15} and \code{N17}}
+\label{sec:goshruns}
+
+\begin{figure}
+
+  \includegraphics[width=\columnwidth]{figs/gosh_rprofs.pdf}
+  \centering
+  \caption{The average of the rms tangential velocity between 1 and \unit{2}{Mm}
+          below each simulations top Schwarzschild boundary as described in
+          \Section{convbound}. The very large oscillations in the tangential velocity
+          in \code{N17} indicate a global oscillation of shell H ingestion is occurring which causes the entrainment rate to
+          increase by up to a factor of 80 (see \Fig{entrain}) during these oscillations.
+          Much milder oscillations can be seen in \code{N15} between 500 and
+          \unit{700}{min} with a modest factor of 3 increase in its entrainment rate. The
+          black line refers to the time when the images of FV in \Fig{renderings} were
+          rendered.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:goshrprofs}
+
+\end{figure}
+
+\begin{figure*}
+
+  \centering
+  % DS: For submission to MNRAS, we have used a lower res image but for final paper, use
+  % full size
+  % \includegraphics[width=\textwidth]{figs/LwZRAWD-merge-lowres.png}
+  \includegraphics[width=\textwidth]{figs/LwZRAWD-merge.pdf}
+  \caption{Both panels show a rendering of the fractional volume FV of
+          the material in the stable layer at $t = \unit{501}{min}$. The C-rich \airfluid{} is
+          transparent. The left panel is from \code{N16}, while the right panel is from
+          \code{N17}. The entrainment rate of H rapidly increases when a global oscillation of shell H ingestion instability
+          occurs in \code{N17}. The hydrodynamic feedback from the energy released from
+          burning causes even more H to be entrained and leads to an unstable runaway in
+          \code{N17} but not in \code{N15}. This is contrasted with the quasi-static
+          entrainment and burning in \code{N16} (\Fig{entrain}).}
+  % Fig made in various notebooks and image manip. software (GIMP) ../notebooks/Renderings
+  \label{fig:renderings}
+
+\end{figure*}
+
+Directly from the entrainment rates of each run in \Fig{entrain}, the
+entrainment rates begin to increase substantially around $t = \unit{300}{min}$
+in both \code{N15} and \code{N17} and continues until $t \approx
+\unit{700}{min}$. \code{N17}'s entrainment rate increases by a factor of up to
+80 during this time compared with its quasi-static rate, while \code{N15}'s
+entrainment rate increases by a factor of up to 3. The cause of these bursts of
+entrainment are due to the collision of opposing horizontal flows forcing
+significant amounts of H-rich material to be entrained in downdrafts where it
+will eventually burn and feedback energy into the flow~\citep{Herwig:2014cx}.
+The magnitude of the horizontal oscillations of these flows is clearly seen in
+\Fig{goshrprofs} where the rms of the tangential velocity rapidly increases and
+decreases within convective turn over timescales. With the same heating rate as
+\code{N15}, \code{N16} does not undergo a global oscillation of shell H ingestion at any point during its entire
+simulation which includes the full duration of the global oscillation of shell H ingestion experienced by
+\code{N15}.
+
+The consequences of the global oscillation of shell H ingestion between \code{N15} and \code{N17} differ
+drastically due to the differences in the amount of H ingested. The weak global oscillation of shell H ingestion of
+\code{N15} does not entrain enough H to sustain it for a long period of time and
+thus it dissipates after \unit{200}{minutes} of large scale oscillations. The
+burning of this additional entrained H is done such that there is very little
+build up of H within the convection zone (\Fig{entrain}) during the global oscillation of shell H ingestion. The
+global oscillation of shell H ingestion does not increase the average tangential velocity significantly over its
+duration and a global oscillation of shell H ingestion does not occur again throughout the \unit{1600}{minute} long
+simulation. Conversely, \code{N17}'s global oscillation of shell H ingestion causes significantly higher
+entrainment of H which is built up within the convection zone. This can be seen
+in the rendering of the fractional volume, FV, at $t = \unit{501}{min}$ in
+\Fig{renderings}. The global oscillation of shell H ingestion subsides briefly after the large build up of H and
+burns most of the H within the convection zone and then begins again at $t =
+\unit{600}{min}$. The simulation is ended soon after the global oscillation of shell H ingestion continues again as
+the expansion of the convection zone has approached where the outer boundary
+condition is applied.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{\mppnp{} post-processing model constraints}
+\label{sec:modelConstraints}
+
+Due to the initial transient at the start of any \ppmstar{} simulation, the
+\mppnp{} post-processing models do not begin until well after this transient has
+finished. This was chosen to be at $\unit{46}{minutes}$ for
+\code{N16} and \code{N17}. The advective mixing models are initialized with an
+$X_{\mathrm{H}}$ profile in the up- and downstreams that is equivalent to the
+spherically averaged $X_{\mathrm{H}}$ profile from the \ppmstar{} simulation.
+The diffusive mixing model is initialized with the spherically averaged
+$X_{\mathrm{H}}$ profile from the \ppmstar{} simulation. For the advective
+post-processing it is not expected that the up- and downstreams would have
+equivalent $X_{\mathrm{H}}$ profiles as seen in \Fig{mollweide}. While running,
+the initial guess of the equivalent profiles in the up- and downstreams is
+quickly changed to the model's preferred profile which is asymmetric (see
+\Fig{advectionprofiles}). This takes around 3 convective turn over timescales
+and causes comparisons with \ppmstar{} profiles to be inaccurate during this
+initialization period. For this reason, all \mppnp{} post-processing models
+repeat the very first time step, with the entrainment rate at that point in
+time, for $\approx 3$ convective turn over timescales so that they establish
+their own quasi-static profile.
+
+The \ppmstar{} simulations output the \textit{briquette}, and any other data
+type, on a \textit{dump} basis. The advective mixing models have their time
+steps being limited by a Courant condition, \eq{courant}, which requires on the
+order of 20-30 time steps being taken for every single \textit{dump} of
+\code{N16}\footnote{\ppmstar{}'s Courant condition is based on the speed of
+sound}. Although the implicit solving of the diffusion equation used by \mppnp{}
+is not limited to a time step criterion like the advective mixing model, all
+post-processing models for a given run, regardless of mixing or network, use the
+advective mixing models Courant condition limited time steps. Both the
+advective and diffusive post-processing models, for a given 3D
+\ppmstar{} run, use the same spherically averaged radial $\rho$, $T$ and $v_{\mathrm{rms}}$
+profiles at a \textit{dump}. Although the stratification and velocity profiles do change
+throughout a \textit{dump} it is negligible as the convective turn over time is
+$\approx \unit{1100}{s}$ for \code{N16}, while the dump interval is $\approx
+\unit{27}{s}$.
+
+As discussed in \Section{convbound}, the CBs in 3D hydrodynamic simulations are
+not a sharp and spherically symmetric boundary as typically interpreted with the
+Schwarzschild criterion. The minimum of the spherical average of $\partial
+v_{\perp} / \partial r$, which can define the location of the CB, could be used
+to determine a time dependent CB for the post-processing models. However, with
+this CB varying at each \textit{dump} in the Eulerian coordinates it is also
+varying in its mass coordinates. Because the advective mixing model requires
+that the mass of the individual cells to remain constant across all time
+(\Section{advectmodel}) this boundary determination can cause the upper and
+lower boundaries to sporadically move between cells on a \textit{dump} basis.
+During a global oscillation of shell H ingestion this boundary determination can lead to a top boundary well within
+the convection zone, as it was determined before it began to global oscillation of shell H ingestion, due to the
+large oscillations in the tangential velocities (see \Fig{goshrprofs}). To
+simplify the definition of the CB and make it applicable to all runs, instead
+the mass coordinates of the initial Schwarzschild boundaries are used to define
+the convective boundaries for all post-processing models. The difference between
+the two boundary criteria is only $\unit{0.43}{Mm}$ at $t = \unit{299}{min}$ for
+\code{N16} (\Tab{ppmstarmodels}). Given that the determination of the tangential
+velocity gradients are from the \textit{briquette} data, which is downsampled
+from the \ppmstar{} simulation and only have a cell length of $\unit{0.18}{Mm}$,
+and the fact that $\sigma_{r_{\mathrm{b}}, v_{\perp}} = \unit{0.46}{Mm}$ for
+that averaged boundary the two boundary determinations are mostly in agreement.
+
+The mass coordinates of the cell interfaces, which are constant for the whole
+duration of the post-processing, are calculated by initially splitting the
+convection zone into equally spaced radial shells in the Eulerian coordinates.
+This makes the mass of individual cells to vary radially but this ensures that
+the sampling of data from the hydro simulations is done at the cell resolution.
+There are approximately $250$ cells for the post-processing models of \code{N16}
+and \code{N17}. The number of cells in \code{N16} was reduced due to the
+computational effort required when using a full network. As the \ppmstar{}
+simulation evolves in time, the density, velocity and radius are interpolated to
+the mass coordinates of the cell interfaces.
+
+\begin{figure}
+
+  \includegraphics[width=\columnwidth]{figs/N16-timescales.pdf}
+  \centering
+  \caption{The radial and horizontal mixing timescales as a function of radius
+          within the convection zone at $t = \unit{299}{min}$ for run \code{N16}.
+          Equations~\ref{eq:radialT} and~\ref{eq:horizontalT} define the radial and
+          horizontal mixing timescales, respectively.}
+  % Fig made in ../notebooks/Results_Hydro/Hydro-Results.ipynb
+  \label{fig:timescales}
+
+\end{figure}
+
+The stream model for \code{N16} was run from $t = \unit{46}{min}$ until the end
+of that simulation at $t = \unit{744}{min}$ resulting in roughly 39
+convective turn over times. The entrainment of the \cldfluid{} into the
+convection zone of the post-processing models is taken directly from the time
+dependent entrainment in \Fig{entrain}. The entrainment rates are small enough
+that the fact that the mass of the convection zone does not change over the
+length of the post-processing model is an accurate approximation to the
+\ppmstar{} simulations. Integrating \code{N16}'s entrainment rate over the
+length of its simulation results in a total of $3.1 \times 10^{-7}\,M_{\odot}$
+of \cldfluid{} being entrained. The cell with the smallest mass within the
+advective post-processing models of \code{N16} is $2.6 \times 10^{-6}\,M_{\odot}$.
+
+\subsection{$\nuclei{12}{C}(\pt,\gamma)\nuclei{13}{N}$-only post-processing models}
+\label{sec:c12pg}
+
+\subsubsection{Diffusive post-processing models}
+\label{sec:Dc12pg}
+
+\begin{figure}
+ \includegraphics[width=\columnwidth]{figs/N16-diff-c12pg-XHrprofs.pdf}
+  \caption{The $X_{\mathrm{H}}$ profiles from \code{N16} and from
+          post-processing models \code{mp9}, using $D_\mathrm{vr}$ according to the recipe
+          provided in \citet{Jones:2017kc}, and \code{mp1}, using $D_\mathrm{FV+vr}$ which
+          inverts the diffusion equation using the spherically-averaged $X_\mathrm{H}$
+          profiles of \ppmstar{} as described in \Section{Dmethod}.}
+  \label{fig:ppmstar-d-compare}
+\end{figure}
+
+Using spherical averages of the $X_{\mathrm{H}}$ and rms of the radial velocity
+from \ppmstar{} the diffusion coefficients $D_{\mathrm{vr}}$ and
+$D_{\mathrm{FV+vr}}$ are computed on a \textit{dump} basis. Using these
+diffusion coefficients in \mppnp{} with only the $\nuclei{12}{C}(\pt,\gamma)\nuclei{13}{N}$
+reaction, the post-processing models of \code{mp1} and \code{mp9} are compared
+with \ppmstar{} in \Fig{ppmstar-d-compare}. Unsurprisingly, the model using the
+$D_{\mathrm{FV+vr}}$ matches the \ppmstar{} profile very closely except right at
+the top CB. This is due to the accuracy of estimating the strength of the mixing
+and the calibration of the entrainment rates. By using the $D_{\mathrm{vr}}$
+diffusion coefficient the mixing near the convective boundary is largely
+overestimated and the mixing near the middle is underestimated. Even though the $|r
+- r_{0}|$ term in \eq{dvr} decreases as the boundary is being approached,
+$D_{\mathrm{vr}}$ does not fall off as quickly as the $D_{\mathrm{FV+vr}}$
+profiles suggest in \Fig{DvrDVF-compare}.
+
+\subsubsection{Advective post-processing models}
+\label{sec:Advc12pg}
+
+From \FigTwo{power-spectrum}{lspectrum} the power spectra of \code{N16} shows
+dominant large-scale modes at the middle of the convection zone as well as a
+more flat spectrum across many scales when near either CB. With the smaller
+modes contributing significantly to the power near the CBs the mixing between
+the two streams is expected to be more efficient there than the middle of the
+convection zone. Applying \eq{horizontalT}, the horizontal and radial timescales
+for run \code{N16} are shown in \Fig{timescales}. The horizontal timescale is
+typically over an order of magnitude larger than the radial timescale suggesting
+inefficient mixing, even at the CBs. There is still significant power at the
+largest modes near the CBs leading to small changes in the horizontal
+timescales across the entire convection zone. The lack of efficient horizontal
+mixing is especially apparent in the middle of the convection zone where the up-
+and downstreams are very isolated from each other as seen in
+\Fig{advectionprofiles}. The upstream is carrying nearly H-free material towards
+the top of the convection zone, while the downstream is carrying H-rich material
+directly to the burning region. This distribution of H-free fluid in the
+upstream and H-rich fluid in the downstream is also validated by the 3D hydro
+simulations as seen in \Fig{mollweide}.
+
+The spherical average of the X$_{\mathrm{H}}$ profiles from the two streams
+closely follows the spherical average of \code{N16} in most regions. However, at
+the very top of the convection zone it is underestimated, while between 16 and
+$\unit{22}{Mm}$ it is overestimated, similarly to the results of the diffusive
+mixing with $D_{\mathrm{vr}}$ (\Fig{ppmstar-d-compare}). One component of this
+is likely due to an underestimation of the horizontal mixing at the top of the
+convection zone. The \textit{briquette} data used to compute the spectra of the
+radial velocity has a resolution that is a factor of 4 smaller than the run's
+grid resolution. This downsampling involves averaging which significantly
+dampens the power in any short wavelength modes, directly increasing the
+horizontal mixing timescale and leading to less efficient mixing. This results
+in much more efficient radial transport of species allowing for the sliver of
+very H-rich material at the top of the convection zone to immediately advect
+downwards rather than be constantly mixed between the two streams.
+
+\begin{figure}
+
+  \includegraphics[width=\columnwidth]{figs/N16-adv-c12pg-XHrprofs.pdf}
+  \includegraphics[width=\columnwidth]{figs/N17-adv-c12pg-XHrprofs.pdf}
+
+  \centering
+  \caption{The top panel is the $X_{\mathrm{H}}$ profiles from \code{N16} and
+          the up- and downstreams of \code{mp2} at $t = \unit{299}{min}$. The spherical
+          average of the up- and downstreams is $\langle \mathrm{Up}, \mathrm{Down}
+          \rangle$. The bottom panel plots the same quantities for \code{N17} and the
+          post-processing model \code{mp4} at $t = \unit{501}{min}$, during the global oscillation of shell H ingestion. The
+          black vertical dotted line is where the integration of the \cldfluid{} is
+          stopped for calculating the entrainment rates in \Fig{entrain}.
+        }
+  % Fig made in ../notebooks/Results_Mppnp/Mppnp-Results.ipynb
+  \label{fig:advectionprofiles}
+
+\end{figure}
+
+\begin{figure}
+
+  \includegraphics[width=\columnwidth]{figs/N16-drhoHdt.pdf}
+  \centering
+  \caption{The burning rate of H per volume as a function of radius
+    for \code{N16}, an advective post-processing model, \code{mp2}, and the 
+    diffusive post-processing models \code{mp1} and \code{mp9}. The $\langle
+    \mathrm{Up}, \mathrm{Down} \rangle$ profile is calculated with the
+    spherical average of the streams to estimate the burning rate,
+    similarly to the estimates from spherically averaged data of
+    \ppmstar{}. The \nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N}
+    reaction is very sensitive to temperature and it does not burn any
+    H until about $\unit{18}{Mm}$ with $\mathrm{T9} = 0.11$. All of
+    the H is burned well before it reaches the bottom of the
+    convection zone.}
+  % Fig made in ../notebooks/Results_Mppnp/Mppnp-Results.ipynb
+  \label{fig:burningrate}
+
+\end{figure}
+
+To better understand the physics of the convective-reactive nucleosynthesis in the RAWD model, 
+it is useful to find out where the H-burning is
+predominately occurring within its He shell. The H burning
+rate at a single time step from the \ppmstar{} simulations and the advective
+post-processing model, \code{mp2}, are estimated in \code{N16} with the
+techniques discussed in \Section{convbound} and is shown in \Fig{burningrate}.
+The advective post-processing model is burning the H a few cells above where
+\code{N16} is burning H. This could suggest that the distribution of flow
+velocities that are present in \ppmstar{} simulations modifies where the bulk of
+the burning takes place within a convection zone. With the fact that there is no
+significant accumulation of H throughout the advective post-processing model it
+is roughly in a quasi-static state in which it is burning all of the H that it ingests.
+
+\subsection{Full network post-processing and comparison with observations}
+\label{sec:fulllnetworkresults}
+
+\begin{figure*}
+
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figs/N16-HN13C13-fnet.pdf}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figs/N16-Kr-isotopes-fnet.pdf}
+  \end{minipage} \\
+
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figs/N17-HN13C13-fnet.pdf}
+  \end{minipage}
+  \begin{minipage}{.49\textwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figs/N17-Kr-isotopes-fnet.pdf}
+  \end{minipage}
+
+  \caption{The top row contains panels using data from the post-processing
+          models of \code{mp5}, \code{mp6} and \code{mp10} (\code{N16}) at $t =
+          \unit{299}{min}$, while the bottom row contains panels using data from the
+          post-processing models of \code{mp7} and \code{mp8} (\code{N17}) at $t =
+          \unit{501}{min}$. In each row, the left panel contains line profiles of the mass
+          fractions of H, \nuclei{13}{N}, and \nuclei{13}{C}, while the right panel
+          contains line profiles of the mass fractions of various Kr isotopes. These
+          isotopes are \nuclei{88}{Kr}, \nuclei{89}{Kr}, and \nuclei{90}{Kr} which have
+          half lives of $\unit{2.84}{hr}$, $\unit{3.18}{minute}$ and $\unit{32.3}{s}$,
+          respectively. The mixing models are distinguished based on line style and glyphs
+          as was done in \FigTwo{ppmstar-d-compare}{advectionprofiles}. $D_{\mathrm{vr}}$
+          profiles are dash-dotted with circles, $D_{\mathrm{FV+vr}}$ profiles are dotted
+          with cross', the upstream profiles are solid with a triangle pointing towards
+          higher radii and the downstream profiles are dashed with a triangle pointing
+          towards lower radii.}
+
+  \label{fig:fnet}
+  % Figs made in ../notebooks/Results_Mppnp/Mppnp-Results.ipynb
+\end{figure*}
+
+\begin{figure}
+
+  \includegraphics[width=\columnwidth]{figs/mp5_bestfit_CS31062-050.pdf}\\
+  \includegraphics[width=\columnwidth]{figs/mp7_bestfit_CS31062-050.pdf}
+  \centering
+  \caption{Both panels show an elemental abundance distribution of the best-fit
+          time for a diffusive post-processing model (\code{mp5} at 0.059 yr for \code{N16} and
+          \code{mp7} at 0.017 yr for \code{N17}) with star CS31062-050~\citep{aoki:02c, johnson:04} as
+          well as the appropriate advective post-processing model at the same simulation
+          time (\code{mp6} for \code{N16} and \code{mp8} for \code{N16}). The top panel
+          plots the models from run \code{N16} with the lower $N_{\mathrm{n}}$ thus taking
+          longer to reach the \nuclei{}{Pb} elemental abundance than the bottom panel
+          which uses models of \code{N17}. The abundances are scaled by the solar
+          abundances from \citet{Asplund2009}.}
+  \label{fig:abu-distri}
+  % Figs made in ../notebooks/PPMstarSEcycles/xsurf_vs_Kimsdata.ipynb
+\end{figure}
+
+With the limitation of only having two fluids in the hydrodynamic simulations
+only the energy feedback from the \nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N}
+reaction can be modeled within them. The 1D advective and diffusive
+post-processing simulations that use the mixing and entrainment calibrated from
+those hydro simulations can model the \ipr~by incorporating a nuclear network with
+thousands of species. With the additional reactions there appear
+sources of neutrons and H at the bottom of the convection zone through the
+\nuclei{13}{C}$(\alpha,n)$\nuclei{16}{O} and various $(\nt, \pt)$ reactions as
+seen in the left panels of \Fig{fnet}. Although not very significant, there is a
+distinction between how the advective and diffusive mixing models behave with
+two burning regions for a given isotope. For \code{N16}, there is the H-burning
+region that ends roughly around \unit{12}{Mm}, where the $X_{\mathrm{H}}$
+reaches a minimum, and then there is the H source from $(\nt, \pt)$ reactions
+that occurs until the bottom CB. The advective mixing model clearly
+distinguishes these two burning regions, while the diffusive mixing model smears
+them, even with time steps that are needed to resolve an explicit
+advective model. Of course, with larger time steps this smearing becomes much
+more significant and the profiles are not properly converged. Another important
+detail with the advective models is that up- and downstreams are distinct in
+not only H but other isotopes as well. As the H is advected down in the
+downstream it burns to produce \nuclei{13}{N} which has a half life of
+approximately \unit{10}{min}. In \code{N16} the convective turn over timescale
+is \unit{18}{min} leading to some of the \nuclei{13}{N} to decay as it moves to
+the bottom CB and then turns over into the upstream. This can also be traced
+with the \nuclei{13}{C} as it is burned while being advected by the downstream to
+the bottom CB. When it eventually moves upwards in the upstream more of the
+\nuclei{13}{N} decays and replenishes the burned \nuclei{13}{C}, and the streams
+become homogenized.
+
+On the right panels of \Fig{fnet} a few unstable Kr isotopes are plotted with
+varying half lives. With the convective turn over timescales of \unit{18}{min}
+and \unit{9}{min} for \code{N16} and \code{N17} respectively the long half life
+of \nuclei{88}{Kr}, \unit{2.84}{hr}, ensures that it is well mixed as its
+Damk\"ohler number ($\mathrm{Da} = \tau_{\mathrm{mix}} /
+\tau_{\mathrm{nuclear}}$) is much less than 1. However for \nuclei{89}{Kr} and
+\nuclei{90}{Kr}, with their half lives of \unit{3.18}{min} and \unit{32.3}{s},
+their Damk\"ohler numbers become greater than 1. With these isotopes the
+distinction between the up- and downstreams becomes apparent and important for
+describing their distribution within the convection zone. Again, the production
+of the neutrons and thus these unstable species is predominately at the bottom
+CB. They are produced when the appropriate $\nt - 1$ isotope is advected down
+and then captures a neutron after which it will predominately be advected away
+in the upstream.
+
+While the hydrodynamic simulations are only able to model the He-shell flash
+convection and the H ingestion for roughly half a day, the latter can last in RAWDs
+roughly for a month~\citep{Denissenkov:19}. A simple approximation for modeling the \ipr~over
+that longer timescale is to assume that the quasi-static behavior of \code{N16}
+will continue, and so the post-processing models are repeated to stretch the integration time. Likewise,
+the \code{N17} simulated behavior can be repeated. The RAWD model G from~\citet{Denissenkov:19},
+on which these simulations are based, had \ipr~yields that were in good
+agreement with the observed elemental abundance distribution in the exemplary
+carbon-enhanced metal poor (CEMP-r/s) star CS31062-050 with seemingly enhanced
+\spr~and \rpr~material. There, a simpler approximation was used to compute the
+\ipr~yields in which a representative time step during the H-ingestion phase was
+used as a static model for \code{mppnp} with the diffusion coefficients provided
+by \code{MESA} \citep{Denissenkov:19, Paxton2011}.
+\Fig{abu-distri} shows the best fit in time of the decayed elemental
+abundance yields from \code{mp5}, and \code{mp7}, with the corresponding
+advective post-processing models \code{mp6} and \code{mp8}, compared with the surface chemical composition of
+CS31062-050 from \cite{aoki:02c} and \cite{johnson:04}. Neither of the advective models has a large enough neutron
+exposure at that point in time to reach the \nuclei{}{Pb} elemental abundances
+observed in that star. 
+The difference in the time it takes for the advective
+model to reach the same \nuclei{}{Pb} abundances as in the diffusive model is approximately 7\%. This is
+of the same order as the inaccuracies in the amount of H ingested and mixed, therefore
+this is not due to differences in how the
+\ipr~nucleosynthesis works in the advective mixing models, but is likely due to
+the numerics (\Section{entrain}). From
+the many RAWD models of \citet{Denissenkov:19} it is clear that the neutron
+density is directly proportional to $\dot{M_{\mathrm{H}}}$ as nearly all of the
+ingested H is burned via \nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} leading to a
+neutron being released. Therefore, the best fit is reached at an earlier time
+for the \code{mp7} run that is based on the \code{N17} simulations with
+the higher H-entrainment rate.
+
+The important result is that even with using the advective method that 
+models mixing in RAWDs closer to what is observed in 3D hydrodynamic simulations
+and uses much better time resolution we can still reproduce the observed chemical
+composition of CS31062-050 well within the H-ingestion timescale of 0.087 yr estimated from
+the 1D stellar evolution computations.
+
+\section{Summary and conclusions}
+\label{sec:conclusions}
+
+In this paper, we described, formulated and applied two different numerical
+methods to model the mixing within a convection zone from 3D hydrodynamic
+simulations in order to compute convective-reactive \ipr~nucleosynthesis. The
+stellar environment of choice was the He shell in a RAWD with a metallicity of
+$\mathrm{[Fe/H]} = -2.6$ (model G of~\citet{Denissenkov:19}). One method used a
+standard 1D diffusive mixing routine, while the other was a two-stream advective
+mixing model that is likened to the models
+of~\citet{cannon1993}~and~\citet{Henkel2017}. These models require mixing
+coefficients which could be taken from estimates using MLT however instead we
+constrain the mixing by running 3D hydrodynamic simulations of the RAWD. The
+mixing coefficients in both models are determined directly from the data of the
+3D hydrodynamic simulations.
+
+The high resolution RAWD simulation, \code{N16}, was run for approximately 39
+convective turn over times showing that its evolution over this timescale to be
+approximately quasi-static. The radial velocity field at $\unit{14.5}{Mm}$ is
+dominated by the large modes of $\ell = 2$ and $3$, while near the CBs the flow
+is spread across many smaller modes (\FigTwo{mollweide}{power-spectrum}). The
+large scale modes encounter the stiff upper boundary and begin to turn over,
+increasing the tangential velocities near the boundaries (\FigTwo{rprofs}{vt-mollweide}). Using
+the gradient of the tangential velocity as a condition for the CB yields a
+spherically averaged boundary at $\unit{23.56}{Mm}$ at $t =
+\unit{299}{minutes}$. This CB is consistent with the CB as determined by the
+initial Schwarzschild boundary of the 3D simulations, which is followed in the
+Lagrangian coordinates, to within a standard deviation of that averaged
+boundary. This is roughly at the resolution of the \textit{briquette} data that
+was used to calculate those boundaries.
+
+The entrainment of \cldfluid{} in \code{N16} is linear in time with an
+entrainment rate of $\dot{M}_{\mathrm{e}} = 7.21 \times
+10^{-12}\,M_{\odot}$\,s$^{-1}$. \code{N15}'s entrainment rate increases by as
+much as a factor of 3 after it experiences a global oscillation of shell H ingestion however it returns to
+quasi-static burning and entrainment as shown in \Fig{entrain}. The global oscillation of shell H ingestion
+instability in \code{N17} causes it go into a feedback loop of rapidly
+increasing entrainment in which it does not return to quasi-static burning and
+entrainment. The entrained H-rich fluid is advected along the downflows to be
+burned rapidly at $\unit{14.5}{Mm}$, while the H-free fluid is advected along the
+upflows. These two fluid mixtures are nearly isolated from each other as there
+is a significant amount of H-free fluid with $X_{\mathrm{H}} \leq
+1\times10^{-6}$ very close to the upper boundary, $\unit{23}{Mm}$, while the
+spherical average is $X_{\mathrm{H}} \approx 1\times10^{-3}$ in the \ppmstar{}
+simulations.
+
+The 1D \mppnp{} post-processing simulations were first applied with only the
+\nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} reaction which is the only reaction
+included in the \ppmstar{} simulations. The instantaneous burning rate of H per
+unit volume is estimated in \code{N16} and \code{mp2} which are in good
+agreement as to where the bulk of the burning occurs.
+The up- and downstreams of \code{mp2} have horizontal mixing timescales that
+are 1-2 dex longer than the radial mixing timescales resulting in the streams
+not homogenizing. Each stream has a distinct $X_{\mathrm{H}}$ radial profile
+that is qualitatively similar to \code{N16}'s distribution of H-free upflows and
+H-rich downflows though not of the same magnitude. The spherical average of the
+two streams is consistent with the \ppmstar{} $X_{\mathrm{H}}$ profiles except
+at the upper boundary where it is underestimated. The difficulty in quantifying
+the convective boundary, the entrainment rate and the spatial averages done in
+the computation of the \textit{briquette} data are possible sources of this
+discrepancy.
+
+With the 1D post-processing models, many more species were included for a more
+elaborate burn network in order to model the \ipr~within the RAWD. The advective
+mixing model sharply distinguishes the two burning regions of H, the
+\nuclei{12}{C}$(\pt,\gamma)$\nuclei{13}{N} sink and the many $(\nt, \pt)$
+sources at the bottom of the convection zone, while the diffusive mixing smears
+these regions even with the time resolution of an explicit advective model.
+However, the consequences of this subtle effect are not clear in this
+application due to numerical errors, which are different for the two models,
+that adjust the amount of H being ingested and accumulated in the convection
+zone. This directly impacts the neutron density in each post-processing
+simulation which results in the advective models requiring more simulation time
+to reach the same neutron exposure as the diffusive models.
+
+For this particular application the sharp distinction between the burning
+regions of H in the advective mixing models played a minor role, which could
+have been masked entirely by the numerical inaccuracies in the ingested H, in
+the \ipr~yields of the RAWD. However this may not be true in the environment of
+C-ingestion into a O shell of a $25\,M_{\odot}$ star~\citep{Ritter2018}. This
+could be a production site for odd Z elements significant enough to influence
+galactic chemical evolution of said elements~\citep{Cote2018}. The many
+different burning layers of $(\gamma, \pt)$ and $(\pt, \gamma)$ that produce the
+odd Z elements may be sensitive to the exact nature of the mixing of these
+species throughout the burning regions to which the advective mixing model would
+be well suited. The non-linearity of the \nuclei{12}{C}$+$\nuclei{12}{C} burning
+could lead to interesting differences in the burning and possible
+nucleosynthesis pathways of the two streams~\citep{Andrassy:19}.
+
+The Fortran advective mixing subroutine used in this work is available at \href{https://github.com/David-Stephens/two-stream-mixing}{Github}.
 
@@
 
-The Acknowledgements section is not numbered. Here you can thank helpful
-colleagues, acknowledge funding agencies, telescopes and facilities used etc.
-Try to keep it short.
+We would like to thank Marco Pignatari and Richard Stancliffe for valuable
+discussions in the early phase of the project. FH acknowledges funding
+from NSERC through a Discovery Grant. This research is supported by
+the National Science Foundation (USA) under Grant No. PHY-1430152
+(JINA Center for the Evolution of the Elements). RA, who completed
+part of this work as a CITA National Fellow, acknowledges support from
+the Canadian Institute for Theoretical Astrophysics and from the Klaus
+Tschira Stiftung. PRW acknowledges NSF grants 1413548
+and AST-1814181. Compute Canada/WestGrid provided the computing and data
+processing resources for this project. Computing time allocations at
+NCSA's Blue Waters and TACC's Frontera machines also contributed to
+this project.
 
+\section*{Data availability and software}
+The data as well as all of the notebooks needed to make all 
+figures of this paper are available on the virtual research platform  
+\url{https://www.ppmstar.org} in the \emph{Public \& Outreach} Jupyter server that 
+is found in the 
+\emph{Hubs} tab. Access is granted via GitHub authentication. The notebooks are located in 
+the directory \code{iRAWD-ATS\_Stephens21}
+of the repository \url{https://github.com/PPMstar/PPMnotebooks}, \code{v0.9}. These notebooks are already preloaded 
+ in the Jupyter session in the directory \code{PPMnotebooks/iRAWD-ATS\_Stephens21}.
+
+The data made available for this project includes the 3D briquette data and amounts to $>\unit{5.8}{TB}$. This data access facility is provided on a best effort basis.
+
+This work benefited from the use of a large amount of
+free/open source software, most importantly the \code{MESA} stellar-evolution code,
+\code{IPython}/\code{Jupyter} notebooks, \code{Docker}, \code{Python} and 
+libraries such as \code{matplotlib}, \code{numpy}, \code{scipy}
+ and \code{pyshtools},
+the \code{FFmpeg} software suite, \code{Subversion} and \code{Git} 
+revision control systems, and the
+\code{LaTeX} document preparation system.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\appendix
-
-\section{Some extra material}
-
-If you want to present additional material which would interrupt the
-flow of the main paper, it can be placed in an Appendix which appears
-after the list of references.
+% \appendix
 
